---
params:
  report_title: ""
  author: ""
  date: ""
  local_authority: ""
  year: ""
  topic_data: ""
  comparison_type: ""
  comparator: ""
title: "`r params$report_title`"
author: "`r params$author`"
date: "`r params$date`"
output:
  pdf_document:
    toc: yes
    fig_caption: false
header-includes:
    - \hypersetup{colorlinks=true, linkcolor = black, urlcolor = [RGB]{0, 163, 163}}
    - \usepackage{titling}
    - \pretitle{\begin{center}
      \includegraphics[width=2in,height=2in]{../www/new_logo.png}\LARGE\\}
    - \posttitle{\end{center}}
    - \renewcommand{\familydefault}{\sfdefault}
classoption: landscape
fontsize: 10pt
papersize: a4
geometry: margin=1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
options(tinytex.verbose = TRUE)

library(knitr)
library(dplyr)
library(kableExtra)
library(png)
library(tidyselect)

local_authority <- params$local_authority
year <- params$year
topic_data <- params$topic_data
comparison_type <- params$comparison_type
comparator <- params$comparator


Table_11.1 <- topic_data[[1]]

Table_11.2 <- topic_data[[2]]

Figure_11.1 <- topic_data[[3]]

Figure_11.2 <- topic_data[[4]]

Table_11.3 <- topic_data[[5]]

Table_11.4 <- topic_data[[6]]

Figure_11.3 <- topic_data[[7]]

Table_11.5 <- topic_data[[8]]

Table_11.6 <- topic_data[[9]]

Table_11.7 <- topic_data[[10]]

Table_11.8 <- topic_data[[11]]

Table_11.9 <- topic_data[[12]]

Table_11.10 <- topic_data[[13]]

Table_11.11 <- topic_data[[14]]

Table_11.12 <- topic_data[[15]]

Figure_11.4 <- topic_data[[16]]

Table_11.13 <- topic_data[[17]]

Table_11.14 <- topic_data[[18]]

Figure_11.5 <- topic_data[[19]]

Table_11.15 <- topic_data[[20]]

Table_11.16 <- topic_data[[21]]

Table_11.17 <- topic_data[[22]]

Table_11.18 <- topic_data[[23]]


main_table_title <- paste0(local_authority, ", ", year)

eval_comparison <- ifelse(comparison_type == "No comparison", FALSE, TRUE)

eval_comparison_time_series <- ifelse(comparison_type == "Year" | comparison_type == "No comparison", FALSE, TRUE)

comparison_table_title <- if (comparison_type == "Local Authority") {
  paste0(comparator, ", ", year)
} else if (comparison_type == "Year") {
  paste0(local_authority, ", ", comparator)
} else {
  NULL
  }

```

## Acknowledgements
The Scottish Government acknowledges and thanks the 10,530
people across Scotland who gave their time to take part in the
Scottish Household Survey 2018.
This report was produced by the Scottish Household Survey Project Team
at the Scottish Government.
We would also like to thank all the Scottish Government lead analysts who
contributed to the project.
Finally, special thanks to Ipsos MORI and their interviewers for continuous
and relentless efforts during the fieldwork.

## Key

```{=latex}
$ \color[RGB]{0, 163, 163} \blacksquare $ Significantly higher $ \color[RGB]{195, 195, 255} \blacksquare $ Significantly lower
```
\pagebreak

## Table 11.1: Whether involved in any Volunteering (Formal or Informal) in the last 12 months by gender
### Column percentages, Adults
### Question first asked in 2018

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.1)) {
Table_11.1 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.1)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.1)) {
if (length(grep("_2", colnames(Table_11.1))) > 0) {
colnames(Table_11.1) <- gsub("%", "\\\\%", colnames(Table_11.1))
main_column_names <- colnames(Table_11.1)[!grepl("_2", colnames(Table_11.1))]
significance_column_names <- colnames(Table_11.1)[grepl("_sig", colnames(Table_11.1))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.1 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.1 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.1)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.1) && length(grep("_2", colnames(Table_11.1))) > 0) {
comparison_column_names <- colnames(Table_11.1)[grepl("_2", colnames(Table_11.1))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.1 %>% select(tidyselect::all_of(colnames(Table_11.1)[!colnames(Table_11.1) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.2: Whether provided unpaid help to organisations or groups in the last 12 months by gender
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.2)) {
Table_11.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.2)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.2)) {
if (length(grep("_2", colnames(Table_11.2))) > 0) {
colnames(Table_11.2) <- gsub("%", "\\\\%", colnames(Table_11.2))
main_column_names <- colnames(Table_11.2)[!grepl("_2", colnames(Table_11.2))]
significance_column_names <- colnames(Table_11.2)[grepl("_sig", colnames(Table_11.2))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.2)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.2) && length(grep("_2", colnames(Table_11.2))) > 0) {
comparison_column_names <- colnames(Table_11.2)[grepl("_2", colnames(Table_11.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.2 %>% select(tidyselect::all_of(colnames(Table_11.2)[!colnames(Table_11.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 11.1: Whether provided unpaid help to organisations or groups in the last 12 months by gender
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_11.1)) {
Figure_11.1 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.1)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_11.1)) {
if (length(grep("_2", colnames(Figure_11.1))) > 0) {
colnames(Figure_11.1) <- gsub("%", "\\\\%", colnames(Figure_11.1))
main_column_names <- colnames(Figure_11.1)[!grepl("_2", colnames(Figure_11.1))]
significance_column_names <- colnames(Figure_11.1)[grepl("_sig", colnames(Figure_11.1))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_11.1 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_11.1 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.1)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_11.1) && length(grep("_2", colnames(Figure_11.1))) > 0) {
comparison_column_names <- colnames(Figure_11.1)[grepl("_2", colnames(Figure_11.1))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_11.1 %>% select(tidyselect::all_of(colnames(Figure_11.1)[!colnames(Figure_11.1) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 11.2: Percentage providing unpaid help to organisations or groups in the last 12 months by age within gender
### Column percentages, Adults
### Split of gender within age is not possible due to base sizes

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_11.2)) {
Figure_11.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.2)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.2)) {
if (length(grep("_2", colnames(Figure_11.2))) > 0) {
colnames(Figure_11.2) <- gsub("%", "\\\\%", colnames(Figure_11.2))
main_column_names <- colnames(Figure_11.2)[!grepl("_2", colnames(Figure_11.2))]
significance_column_names <- colnames(Figure_11.2)[grepl("_sig", colnames(Figure_11.2))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_11.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#00A3A3", `40-64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#00A3A3", `65+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_11.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.2)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.2) && length(grep("_2", colnames(Figure_11.2))) > 0) {
comparison_column_names <- colnames(Figure_11.2)[grepl("_2", colnames(Figure_11.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_11.2 %>% select(tidyselect::all_of(colnames(Figure_11.2)[!colnames(Figure_11.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#C3C3FF", `40-64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#C3C3FF", `65+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.3: Whether provided unpaid help to organisations or groups in the last 12 months by current economic situation
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.3)) {
Table_11.3 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.3)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.3)) {
if (length(grep("_2", colnames(Table_11.3))) > 0) {
colnames(Table_11.3) <- gsub("%", "\\\\%", colnames(Table_11.3))
main_column_names <- colnames(Table_11.3)[!grepl("_2", colnames(Table_11.3))]
significance_column_names <- colnames(Table_11.3)[grepl("_sig", colnames(Table_11.3))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.3 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Self employed/full-/part-/time employment` = cell_spec(`Self employed/full-/part-/time employment`, "latex", background = case_when(`Self employed/full-/part-/time employment_sig` == "HIGHER" ~ "#00A3A3", `Self employed/full-/part-/time employment_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Other` = cell_spec(`Other`, "latex", background = case_when(`Other_sig` == "HIGHER" ~ "#00A3A3", `Other_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Permanently retired from work` = cell_spec(`Permanently retired from work`, "latex", background = case_when(`Permanently retired from work_sig` == "HIGHER" ~ "#00A3A3", `Permanently retired from work_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.3 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.3)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.3) && length(grep("_2", colnames(Table_11.3))) > 0) {
comparison_column_names <- colnames(Table_11.3)[grepl("_2", colnames(Table_11.3))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.3 %>% select(tidyselect::all_of(colnames(Table_11.3)[!colnames(Table_11.3) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Self employed/full-/part-/time employment` = cell_spec(`Self employed/full-/part-/time employment`, "latex", background = case_when(`Self employed/full-/part-/time employment_sig` == "HIGHER" ~ "#C3C3FF", `Self employed/full-/part-/time employment_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Other` = cell_spec(`Other`, "latex", background = case_when(`Other_sig` == "HIGHER" ~ "#C3C3FF", `Other_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Permanently retired from work` = cell_spec(`Permanently retired from work`, "latex", background = case_when(`Permanently retired from work_sig` == "HIGHER" ~ "#C3C3FF", `Permanently retired from work_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.4: Whether provided unpaid help to organisations or groups in the last 12 months by net annual household income
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.4)) {
Table_11.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.4)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.4)) {
if (length(grep("_2", colnames(Table_11.4))) > 0) {
colnames(Table_11.4) <- gsub("%", "\\\\%", colnames(Table_11.4))
main_column_names <- colnames(Table_11.4)[!grepl("_2", colnames(Table_11.4))]
significance_column_names <- colnames(Table_11.4)[grepl("_sig", colnames(Table_11.4))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.4 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Up to £15,000` = cell_spec(`Up to £15,000`, "latex", background = case_when(`Up to £15,000_sig` == "HIGHER" ~ "#00A3A3", `Up to £15,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`£15,001 to £30,000` = cell_spec(`£15,001 to £30,000`, "latex", background = case_when(`£15,001 to £30,000_sig` == "HIGHER" ~ "#00A3A3", `£15,001 to £30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Over £30,000` = cell_spec(`Over £30,000`, "latex", background = case_when(`Over £30,000_sig` == "HIGHER" ~ "#00A3A3", `Over £30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.4)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.4) && length(grep("_2", colnames(Table_11.4))) > 0) {
comparison_column_names <- colnames(Table_11.4)[grepl("_2", colnames(Table_11.4))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.4 %>% select(tidyselect::all_of(colnames(Table_11.4)[!colnames(Table_11.4) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Up to £15,000` = cell_spec(`Up to £15,000`, "latex", background = case_when(`Up to £15,000_sig` == "HIGHER" ~ "#C3C3FF", `Up to £15,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`£15,001 to £30,000` = cell_spec(`£15,001 to £30,000`, "latex", background = case_when(`£15,001 to £30,000_sig` == "HIGHER" ~ "#C3C3FF", `£15,001 to £30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Over £30,000` = cell_spec(`Over £30,000`, "latex", background = case_when(`Over £30,000_sig` == "HIGHER" ~ "#C3C3FF", `Over £30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 11.3: Whether provided unpaid help to organisations or groups in the last 12 months by Scottish Index of Multiple Deprivation
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_11.3)) {
Figure_11.3 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.3)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.3)) {
if (length(grep("_2", colnames(Figure_11.3))) > 0) {
colnames(Figure_11.3) <- gsub("%", "\\\\%", colnames(Figure_11.3))
main_column_names <- colnames(Figure_11.3)[!grepl("_2", colnames(Figure_11.3))]
significance_column_names <- colnames(Figure_11.3)[grepl("_sig", colnames(Figure_11.3))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_11.3 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1 - 20\\% most deprived` = cell_spec(`1 - 20\\% most deprived`, "latex", background = case_when(`1 - 20\\% most deprived_sig` == "HIGHER" ~ "#00A3A3", `1 - 20\\% most deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#00A3A3", `2_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#00A3A3", `3_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#00A3A3", `4_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`5 - 20\\% least deprived` = cell_spec(`5 - 20\\% least deprived`, "latex", background = case_when(`5 - 20\\% least deprived_sig` == "HIGHER" ~ "#00A3A3", `5 - 20\\% least deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_11.3 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.3)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.3) && length(grep("_2", colnames(Figure_11.3))) > 0) {
comparison_column_names <- colnames(Figure_11.3)[grepl("_2", colnames(Figure_11.3))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_11.3 %>% select(tidyselect::all_of(colnames(Figure_11.3)[!colnames(Figure_11.3) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1 - 20\\% most deprived` = cell_spec(`1 - 20\\% most deprived`, "latex", background = case_when(`1 - 20\\% most deprived_sig` == "HIGHER" ~ "#C3C3FF", `1 - 20\\% most deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#C3C3FF", `2_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#C3C3FF", `3_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#C3C3FF", `4_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`5 - 20\\% least deprived` = cell_spec(`5 - 20\\% least deprived`, "latex", background = case_when(`5 - 20\\% least deprived_sig` == "HIGHER" ~ "#C3C3FF", `5 - 20\\% least deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.5: Whether provided unpaid help to organisations or groups in the last 12 months by Urban/Rural classification
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.5)) {
Table_11.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.5)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.5)) {
if (length(grep("_2", colnames(Table_11.5))) > 0) {
colnames(Table_11.5) <- gsub("%", "\\\\%", colnames(Table_11.5))
main_column_names <- colnames(Table_11.5)[!grepl("_2", colnames(Table_11.5))]
significance_column_names <- colnames(Table_11.5)[grepl("_sig", colnames(Table_11.5))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.5 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Large urban areas` = cell_spec(`Large urban areas`, "latex", background = case_when(`Large urban areas_sig` == "HIGHER" ~ "#00A3A3", `Large urban areas_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Other urban areas` = cell_spec(`Other urban areas`, "latex", background = case_when(`Other urban areas_sig` == "HIGHER" ~ "#00A3A3", `Other urban areas_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Accessible small towns` = cell_spec(`Accessible small towns`, "latex", background = case_when(`Accessible small towns_sig` == "HIGHER" ~ "#00A3A3", `Accessible small towns_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Remote small towns` = cell_spec(`Remote small towns`, "latex", background = case_when(`Remote small towns_sig` == "HIGHER" ~ "#00A3A3", `Remote small towns_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Accessible rural` = cell_spec(`Accessible rural`, "latex", background = case_when(`Accessible rural_sig` == "HIGHER" ~ "#00A3A3", `Accessible rural_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Remote rural` = cell_spec(`Remote rural`, "latex", background = case_when(`Remote rural_sig` == "HIGHER" ~ "#00A3A3", `Remote rural_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.5)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.5) && length(grep("_2", colnames(Table_11.5))) > 0) {
comparison_column_names <- colnames(Table_11.5)[grepl("_2", colnames(Table_11.5))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.5 %>% select(tidyselect::all_of(colnames(Table_11.5)[!colnames(Table_11.5) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Large urban areas` = cell_spec(`Large urban areas`, "latex", background = case_when(`Large urban areas_sig` == "HIGHER" ~ "#C3C3FF", `Large urban areas_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Other urban areas` = cell_spec(`Other urban areas`, "latex", background = case_when(`Other urban areas_sig` == "HIGHER" ~ "#C3C3FF", `Other urban areas_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Accessible small towns` = cell_spec(`Accessible small towns`, "latex", background = case_when(`Accessible small towns_sig` == "HIGHER" ~ "#C3C3FF", `Accessible small towns_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Remote small towns` = cell_spec(`Remote small towns`, "latex", background = case_when(`Remote small towns_sig` == "HIGHER" ~ "#C3C3FF", `Remote small towns_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Accessible rural` = cell_spec(`Accessible rural`, "latex", background = case_when(`Accessible rural_sig` == "HIGHER" ~ "#C3C3FF", `Accessible rural_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Remote rural` = cell_spec(`Remote rural`, "latex", background = case_when(`Remote rural_sig` == "HIGHER" ~ "#C3C3FF", `Remote rural_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.6: Types of organizations or groups for which adults provided help in the last 12 months by Urban/Rural classification
### Column percentages, Adults
### Columns may add up to more than 100 per cent as multiple responses were allowed
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.6)) {
Table_11.6 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.6)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.6)) {
if (length(grep("_2", colnames(Table_11.6))) > 0) {
colnames(Table_11.6) <- gsub("%", "\\\\%", colnames(Table_11.6))
main_column_names <- colnames(Table_11.6)[!grepl("_2", colnames(Table_11.6))]
significance_column_names <- colnames(Table_11.6)[grepl("_sig", colnames(Table_11.6))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.6 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Large urban areas` = cell_spec(`Large urban areas`, "latex", background = case_when(`Large urban areas_sig` == "HIGHER" ~ "#00A3A3", `Large urban areas_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Other urban areas` = cell_spec(`Other urban areas`, "latex", background = case_when(`Other urban areas_sig` == "HIGHER" ~ "#00A3A3", `Other urban areas_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Accessible small towns` = cell_spec(`Accessible small towns`, "latex", background = case_when(`Accessible small towns_sig` == "HIGHER" ~ "#00A3A3", `Accessible small towns_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Remote small towns` = cell_spec(`Remote small towns`, "latex", background = case_when(`Remote small towns_sig` == "HIGHER" ~ "#00A3A3", `Remote small towns_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Accessible rural` = cell_spec(`Accessible rural`, "latex", background = case_when(`Accessible rural_sig` == "HIGHER" ~ "#00A3A3", `Accessible rural_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Remote rural` = cell_spec(`Remote rural`, "latex", background = case_when(`Remote rural_sig` == "HIGHER" ~ "#00A3A3", `Remote rural_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
Table_11.6 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.6)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.6) && length(grep("_2", colnames(Table_11.6))) > 0) {
comparison_column_names <- colnames(Table_11.6)[grepl("_2", colnames(Table_11.6))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.6 %>% select(tidyselect::all_of(colnames(Table_11.6)[!colnames(Table_11.6) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Large urban areas` = cell_spec(`Large urban areas`, "latex", background = case_when(`Large urban areas_sig` == "HIGHER" ~ "#C3C3FF", `Large urban areas_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Other urban areas` = cell_spec(`Other urban areas`, "latex", background = case_when(`Other urban areas_sig` == "HIGHER" ~ "#C3C3FF", `Other urban areas_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Accessible small towns` = cell_spec(`Accessible small towns`, "latex", background = case_when(`Accessible small towns_sig` == "HIGHER" ~ "#C3C3FF", `Accessible small towns_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Remote small towns` = cell_spec(`Remote small towns`, "latex", background = case_when(`Remote small towns_sig` == "HIGHER" ~ "#C3C3FF", `Remote small towns_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Accessible rural` = cell_spec(`Accessible rural`, "latex", background = case_when(`Accessible rural_sig` == "HIGHER" ~ "#C3C3FF", `Accessible rural_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Remote rural` = cell_spec(`Remote rural`, "latex", background = case_when(`Remote rural_sig` == "HIGHER" ~ "#C3C3FF", `Remote rural_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.7: Types of organisations or groups for which adults provided help in the last 12 months by age and gender
### Column percentages, Adults
### Columns may add up to more than 100 per cent as multiple responses were allowed
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.7)) {
Table_11.7 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.7)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.7)) {
if (length(grep("_2", colnames(Table_11.7))) > 0) {
colnames(Table_11.7) <- gsub("%", "\\\\%", colnames(Table_11.7))
main_column_names <- colnames(Table_11.7)[!grepl("_2", colnames(Table_11.7))]
significance_column_names <- colnames(Table_11.7)[grepl("_sig", colnames(Table_11.7))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.7 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#00A3A3", `40-64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#00A3A3", `65+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
Table_11.7 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.7)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.7) && length(grep("_2", colnames(Table_11.7))) > 0) {
comparison_column_names <- colnames(Table_11.7)[grepl("_2", colnames(Table_11.7))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.7 %>% select(tidyselect::all_of(colnames(Table_11.7)[!colnames(Table_11.7) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#C3C3FF", `40-64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#C3C3FF", `65+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.8: Types of work / unpaid activity adults have undertaken in the last 12 months by age and gender
### Column percentages, Adults
### Columns may add up to more than 100 per cent as multiple responses were allowed

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.8)) {
Table_11.8 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.8)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.8)) {
if (length(grep("_2", colnames(Table_11.8))) > 0) {
colnames(Table_11.8) <- gsub("%", "\\\\%", colnames(Table_11.8))
main_column_names <- colnames(Table_11.8)[!grepl("_2", colnames(Table_11.8))]
significance_column_names <- colnames(Table_11.8)[grepl("_sig", colnames(Table_11.8))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.8 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#00A3A3", `40-64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#00A3A3", `65+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
Table_11.8 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.8)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.8) && length(grep("_2", colnames(Table_11.8))) > 0) {
comparison_column_names <- colnames(Table_11.8)[grepl("_2", colnames(Table_11.8))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.8 %>% select(tidyselect::all_of(colnames(Table_11.8)[!colnames(Table_11.8) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#C3C3FF", `40-64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#C3C3FF", `65+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.9: Frequency of unpaid help to organisations or groups in the last 12 months by age and gender
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.9)) {
Table_11.9 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.9)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.9)) {
if (length(grep("_2", colnames(Table_11.9))) > 0) {
colnames(Table_11.9) <- gsub("%", "\\\\%", colnames(Table_11.9))
main_column_names <- colnames(Table_11.9)[!grepl("_2", colnames(Table_11.9))]
significance_column_names <- colnames(Table_11.9)[grepl("_sig", colnames(Table_11.9))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.9 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#00A3A3", `40-64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#00A3A3", `65+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.9 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.9)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.9) && length(grep("_2", colnames(Table_11.9))) > 0) {
comparison_column_names <- colnames(Table_11.9)[grepl("_2", colnames(Table_11.9))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.9 %>% select(tidyselect::all_of(colnames(Table_11.9)[!colnames(Table_11.9) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#C3C3FF", `40-64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#C3C3FF", `65+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.10: Total number of hours of unpaid work provided in the past month
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.10)) {
Table_11.10 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.10)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.10)) {
if (length(grep("_2", colnames(Table_11.10))) > 0) {
colnames(Table_11.10) <- gsub("%", "\\\\%", colnames(Table_11.10))
main_column_names <- colnames(Table_11.10)[!grepl("_2", colnames(Table_11.10))]
significance_column_names <- colnames(Table_11.10)[grepl("_sig", colnames(Table_11.10))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.10 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.10 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.10)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.10) && length(grep("_2", colnames(Table_11.10))) > 0) {
comparison_column_names <- colnames(Table_11.10)[grepl("_2", colnames(Table_11.10))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.10 %>% select(tidyselect::all_of(colnames(Table_11.10)[!colnames(Table_11.10) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.11: Reasons why adults may undertake unpaid help in the future
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.11)) {
Table_11.11 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.11)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.11)) {
if (length(grep("_2", colnames(Table_11.11))) > 0) {
colnames(Table_11.11) <- gsub("%", "\\\\%", colnames(Table_11.11))
main_column_names <- colnames(Table_11.11)[!grepl("_2", colnames(Table_11.11))]
significance_column_names <- colnames(Table_11.11)[grepl("_sig", colnames(Table_11.11))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.11 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
Table_11.11 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.11)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.11) && length(grep("_2", colnames(Table_11.11))) > 0) {
comparison_column_names <- colnames(Table_11.11)[grepl("_2", colnames(Table_11.11))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.11 %>% select(tidyselect::all_of(colnames(Table_11.11)[!colnames(Table_11.11) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.12: Whether involved in any Informal Volunteering in the last 12 months by gender
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.12)) {
Table_11.12 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.12)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.12)) {
if (length(grep("_2", colnames(Table_11.12))) > 0) {
colnames(Table_11.12) <- gsub("%", "\\\\%", colnames(Table_11.12))
main_column_names <- colnames(Table_11.12)[!grepl("_2", colnames(Table_11.12))]
significance_column_names <- colnames(Table_11.12)[grepl("_sig", colnames(Table_11.12))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.12 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.12 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.12)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.12) && length(grep("_2", colnames(Table_11.12))) > 0) {
comparison_column_names <- colnames(Table_11.12)[grepl("_2", colnames(Table_11.12))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.12 %>% select(tidyselect::all_of(colnames(Table_11.12)[!colnames(Table_11.12) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 11.4: Whether involved in any Informal Volunteering in the last 12 months by age within gender
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_11.4)) {
Figure_11.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.4)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.4)) {
if (length(grep("_2", colnames(Figure_11.4))) > 0) {
colnames(Figure_11.4) <- gsub("%", "\\\\%", colnames(Figure_11.4))
main_column_names <- colnames(Figure_11.4)[!grepl("_2", colnames(Figure_11.4))]
significance_column_names <- colnames(Figure_11.4)[grepl("_sig", colnames(Figure_11.4))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_11.4 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_11.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.4)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.4) && length(grep("_2", colnames(Figure_11.4))) > 0) {
comparison_column_names <- colnames(Figure_11.4)[grepl("_2", colnames(Figure_11.4))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_11.4 %>% select(tidyselect::all_of(colnames(Figure_11.4)[!colnames(Figure_11.4) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.13: Whether involved in any Informal Volunteering in the last 12 months by current economic status
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.13)) {
Table_11.13 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.13)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.13)) {
if (length(grep("_2", colnames(Table_11.13))) > 0) {
colnames(Table_11.13) <- gsub("%", "\\\\%", colnames(Table_11.13))
main_column_names <- colnames(Table_11.13)[!grepl("_2", colnames(Table_11.13))]
significance_column_names <- colnames(Table_11.13)[grepl("_sig", colnames(Table_11.13))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.13 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Self employed/full-/part-/time employment` = cell_spec(`Self employed/full-/part-/time employment`, "latex", background = case_when(`Self employed/full-/part-/time employment_sig` == "HIGHER" ~ "#00A3A3", `Self employed/full-/part-/time employment_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Other` = cell_spec(`Other`, "latex", background = case_when(`Other_sig` == "HIGHER" ~ "#00A3A3", `Other_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Permanently retired from work` = cell_spec(`Permanently retired from work`, "latex", background = case_when(`Permanently retired from work_sig` == "HIGHER" ~ "#00A3A3", `Permanently retired from work_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.13 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.13)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.13) && length(grep("_2", colnames(Table_11.13))) > 0) {
comparison_column_names <- colnames(Table_11.13)[grepl("_2", colnames(Table_11.13))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.13 %>% select(tidyselect::all_of(colnames(Table_11.13)[!colnames(Table_11.13) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Self employed/full-/part-/time employment` = cell_spec(`Self employed/full-/part-/time employment`, "latex", background = case_when(`Self employed/full-/part-/time employment_sig` == "HIGHER" ~ "#C3C3FF", `Self employed/full-/part-/time employment_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Other` = cell_spec(`Other`, "latex", background = case_when(`Other_sig` == "HIGHER" ~ "#C3C3FF", `Other_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Permanently retired from work` = cell_spec(`Permanently retired from work`, "latex", background = case_when(`Permanently retired from work_sig` == "HIGHER" ~ "#C3C3FF", `Permanently retired from work_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.14: Whether involved in any Informal Volunteering in the last 12 months by net annual income
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.14)) {
Table_11.14 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.14)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.14)) {
if (length(grep("_2", colnames(Table_11.14))) > 0) {
colnames(Table_11.14) <- gsub("%", "\\\\%", colnames(Table_11.14))
main_column_names <- colnames(Table_11.14)[!grepl("_2", colnames(Table_11.14))]
significance_column_names <- colnames(Table_11.14)[grepl("_sig", colnames(Table_11.14))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.14 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Up to £15,000` = cell_spec(`Up to £15,000`, "latex", background = case_when(`Up to £15,000_sig` == "HIGHER" ~ "#00A3A3", `Up to £15,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`£15,001 to £30,000` = cell_spec(`£15,001 to £30,000`, "latex", background = case_when(`£15,001 to £30,000_sig` == "HIGHER" ~ "#00A3A3", `£15,001 to £30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Over £30,000` = cell_spec(`Over £30,000`, "latex", background = case_when(`Over £30,000_sig` == "HIGHER" ~ "#00A3A3", `Over £30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.14 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.14)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.14) && length(grep("_2", colnames(Table_11.14))) > 0) {
comparison_column_names <- colnames(Table_11.14)[grepl("_2", colnames(Table_11.14))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.14 %>% select(tidyselect::all_of(colnames(Table_11.14)[!colnames(Table_11.14) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Up to £15,000` = cell_spec(`Up to £15,000`, "latex", background = case_when(`Up to £15,000_sig` == "HIGHER" ~ "#C3C3FF", `Up to £15,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`£15,001 to £30,000` = cell_spec(`£15,001 to £30,000`, "latex", background = case_when(`£15,001 to £30,000_sig` == "HIGHER" ~ "#C3C3FF", `£15,001 to £30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Over £30,000` = cell_spec(`Over £30,000`, "latex", background = case_when(`Over £30,000_sig` == "HIGHER" ~ "#C3C3FF", `Over £30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 11.5: Whether involved in any Informal Volunteering in the last 12 months by Scottish Index of Multiple Deprivation
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_11.5)) {
Figure_11.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.5)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.5)) {
if (length(grep("_2", colnames(Figure_11.5))) > 0) {
colnames(Figure_11.5) <- gsub("%", "\\\\%", colnames(Figure_11.5))
main_column_names <- colnames(Figure_11.5)[!grepl("_2", colnames(Figure_11.5))]
significance_column_names <- colnames(Figure_11.5)[grepl("_sig", colnames(Figure_11.5))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_11.5 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1 - 20\\% most deprived` = cell_spec(`1 - 20\\% most deprived`, "latex", background = case_when(`1 - 20\\% most deprived_sig` == "HIGHER" ~ "#00A3A3", `1 - 20\\% most deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#00A3A3", `2_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#00A3A3", `3_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#00A3A3", `4_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`5 - 20\\% least deprived` = cell_spec(`5 - 20\\% least deprived`, "latex", background = case_when(`5 - 20\\% least deprived_sig` == "HIGHER" ~ "#00A3A3", `5 - 20\\% least deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_11.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_11.5)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_11.5) && length(grep("_2", colnames(Figure_11.5))) > 0) {
comparison_column_names <- colnames(Figure_11.5)[grepl("_2", colnames(Figure_11.5))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_11.5 %>% select(tidyselect::all_of(colnames(Figure_11.5)[!colnames(Figure_11.5) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1 - 20\\% most deprived` = cell_spec(`1 - 20\\% most deprived`, "latex", background = case_when(`1 - 20\\% most deprived_sig` == "HIGHER" ~ "#C3C3FF", `1 - 20\\% most deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#C3C3FF", `2_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#C3C3FF", `3_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#C3C3FF", `4_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`5 - 20\\% least deprived` = cell_spec(`5 - 20\\% least deprived`, "latex", background = case_when(`5 - 20\\% least deprived_sig` == "HIGHER" ~ "#C3C3FF", `5 - 20\\% least deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.15: Whether involved in any Informal Volunteering in the last 12 months by Urban/Rural classification
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.15)) {
Table_11.15 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.15)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.15)) {
if (length(grep("_2", colnames(Table_11.15))) > 0) {
colnames(Table_11.15) <- gsub("%", "\\\\%", colnames(Table_11.15))
main_column_names <- colnames(Table_11.15)[!grepl("_2", colnames(Table_11.15))]
significance_column_names <- colnames(Table_11.15)[grepl("_sig", colnames(Table_11.15))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.15 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Large urban areas` = cell_spec(`Large urban areas`, "latex", background = case_when(`Large urban areas_sig` == "HIGHER" ~ "#00A3A3", `Large urban areas_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Other urban areas` = cell_spec(`Other urban areas`, "latex", background = case_when(`Other urban areas_sig` == "HIGHER" ~ "#00A3A3", `Other urban areas_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Accessible small towns` = cell_spec(`Accessible small towns`, "latex", background = case_when(`Accessible small towns_sig` == "HIGHER" ~ "#00A3A3", `Accessible small towns_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Remote small towns` = cell_spec(`Remote small towns`, "latex", background = case_when(`Remote small towns_sig` == "HIGHER" ~ "#00A3A3", `Remote small towns_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Accessible rural` = cell_spec(`Accessible rural`, "latex", background = case_when(`Accessible rural_sig` == "HIGHER" ~ "#00A3A3", `Accessible rural_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Remote rural` = cell_spec(`Remote rural`, "latex", background = case_when(`Remote rural_sig` == "HIGHER" ~ "#00A3A3", `Remote rural_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.15 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.15)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.15) && length(grep("_2", colnames(Table_11.15))) > 0) {
comparison_column_names <- colnames(Table_11.15)[grepl("_2", colnames(Table_11.15))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.15 %>% select(tidyselect::all_of(colnames(Table_11.15)[!colnames(Table_11.15) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Large urban areas` = cell_spec(`Large urban areas`, "latex", background = case_when(`Large urban areas_sig` == "HIGHER" ~ "#C3C3FF", `Large urban areas_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Other urban areas` = cell_spec(`Other urban areas`, "latex", background = case_when(`Other urban areas_sig` == "HIGHER" ~ "#C3C3FF", `Other urban areas_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Accessible small towns` = cell_spec(`Accessible small towns`, "latex", background = case_when(`Accessible small towns_sig` == "HIGHER" ~ "#C3C3FF", `Accessible small towns_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Remote small towns` = cell_spec(`Remote small towns`, "latex", background = case_when(`Remote small towns_sig` == "HIGHER" ~ "#C3C3FF", `Remote small towns_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Accessible rural` = cell_spec(`Accessible rural`, "latex", background = case_when(`Accessible rural_sig` == "HIGHER" ~ "#C3C3FF", `Accessible rural_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Remote rural` = cell_spec(`Remote rural`, "latex", background = case_when(`Remote rural_sig` == "HIGHER" ~ "#C3C3FF", `Remote rural_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.16: Types of Informal Volunteering activity in the last 12 months by gender and age
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.16)) {
Table_11.16 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.16)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.16)) {
if (length(grep("_2", colnames(Table_11.16))) > 0) {
colnames(Table_11.16) <- gsub("%", "\\\\%", colnames(Table_11.16))
main_column_names <- colnames(Table_11.16)[!grepl("_2", colnames(Table_11.16))]
significance_column_names <- colnames(Table_11.16)[grepl("_sig", colnames(Table_11.16))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.16 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#00A3A3", `40-64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#00A3A3", `65+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
Table_11.16 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.16)), escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.16) && length(grep("_2", colnames(Table_11.16))) > 0) {
comparison_column_names <- colnames(Table_11.16)[grepl("_2", colnames(Table_11.16))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.16 %>% select(tidyselect::all_of(colnames(Table_11.16)[!colnames(Table_11.16) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#C3C3FF", `40-64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#C3C3FF", `65+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.17: Frequency of Informal Volunteering in the last 12 months by gender and age
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.17)) {
Table_11.17 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.17)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.17)) {
if (length(grep("_2", colnames(Table_11.17))) > 0) {
colnames(Table_11.17) <- gsub("%", "\\\\%", colnames(Table_11.17))
main_column_names <- colnames(Table_11.17)[!grepl("_2", colnames(Table_11.17))]
significance_column_names <- colnames(Table_11.17)[grepl("_sig", colnames(Table_11.17))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.17 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#00A3A3", `40-64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#00A3A3", `65+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.17 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.17)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.17) && length(grep("_2", colnames(Table_11.17))) > 0) {
comparison_column_names <- colnames(Table_11.17)[grepl("_2", colnames(Table_11.17))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.17 %>% select(tidyselect::all_of(colnames(Table_11.17)[!colnames(Table_11.17) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#C3C3FF", `40-64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#C3C3FF", `65+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 11.18: Total number of Informal Volunteering hours in the last 12 months
### Column percentages, Adults
### [See 2017 LA tables for historic data due to wording changes](https://www2.gov.scot/Topics/Statistics/16002/LAtables2017)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_11.18)) {
Table_11.18 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.18)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_11.18)) {
if (length(grep("_2", colnames(Table_11.18))) > 0) {
colnames(Table_11.18) <- gsub("%", "\\\\%", colnames(Table_11.18))
main_column_names <- colnames(Table_11.18)[!grepl("_2", colnames(Table_11.18))]
significance_column_names <- colnames(Table_11.18)[grepl("_sig", colnames(Table_11.18))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_11.18 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_11.18 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_11.18)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_11.18) && length(grep("_2", colnames(Table_11.18))) > 0) {
comparison_column_names <- colnames(Table_11.18)[grepl("_2", colnames(Table_11.18))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_11.18 %>% select(tidyselect::all_of(colnames(Table_11.18)[!colnames(Table_11.18) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

