---
params:
  report_title: ""
  local_authority: ""
  year: ""
  topic_data: ""
  comparison_type: ""
  comparator: ""
title: "`r params$report_title`"
output:
  pdf_document:
    toc: yes
    fig_caption: false
header-includes:
    - \hypersetup{colorlinks=true, linkcolor = black, urlcolor = [RGB]{0, 163, 163}}
    - \usepackage{titling}
    - \pretitle{\begin{center}
      \includegraphics[width=2in,height=2in]{../www/new_logo.png}\LARGE\\}
    - \posttitle{\end{center}}
    - \renewcommand{\familydefault}{\sfdefault}
classoption: landscape
fontsize: 10pt
papersize: a4
geometry: margin=1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
options(tinytex.verbose = TRUE)

library(knitr)
library(dplyr)
library(kableExtra)
library(png)
library(tidyselect)

local_authority <- params$local_authority
year <- params$year
topic_data <- params$topic_data
comparison_type <- params$comparison_type
comparator <- params$comparator

Table_2.1 <- topic_data[[1]]
Table_2.2 <- topic_data[[2]]
Table_2.3 <- topic_data[[3]]
Figure_2.1 <- topic_data[[4]]
Figure_2.2 <- topic_data[[5]]
Table_2.4_Figure_2.3 <- topic_data[[6]]
Table_2.5 <- topic_data[[7]]
Table_2.6 <- topic_data[[8]]
Figure_2.4 <- topic_data[[9]]
Table_2.7 <- topic_data[[10]]
Figure_2.5 <- topic_data[[11]]
Table_2.8 <- topic_data[[12]]
Table_2.9 <- topic_data[[13]]
Table_2.10 <- topic_data[[14]]
Table_2.11 <- topic_data[[15]]
Table_2.12 <- topic_data[[16]]
Table_2.13 <- topic_data[[17]]
Table_2.14 <- topic_data[[18]]
Table_2.15 <- topic_data[[19]]
Table_2.16 <- topic_data[[20]]
Table_2.17 <- topic_data[[21]]

main_table_title <- paste0(local_authority, ", ", year)

eval_comparison <- ifelse(comparison_type == "No comparison", FALSE, TRUE)

eval_comparison_time_series <- ifelse(comparison_type == "Year" | comparison_type == "No comparison", FALSE, TRUE)

comparison_table_title <- if (comparison_type == "Local Authority") {
  paste0(comparator, ", ", year)
} else if (comparison_type == "Year") {
  paste0(local_authority, ", ", comparator)
} else {
  NULL
  }

```

## Acknowledgements
The Scottish Government acknowledges and thanks the 10,530
people across Scotland who gave their time to take part in the
Scottish Household Survey 2018.
This report was produced by the Scottish Household Survey Project Team
at the Scottish Government.
We would also like to thank all the Scottish Government lead analysts who
contributed to the project.
Finally, special thanks to Ipsos MORI and their interviewers for continuous
and relentless efforts during the fieldwork.

## Key

```{=latex}
$ \color[RGB]{0, 163, 163} \blacksquare $ Significantly higher $ \color[RGB]{195, 195, 255} \blacksquare $ Significantly lower
```
## Table 2.1: Age of all household members by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.1)) {
Table_2.1 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.1)) {
if (length(grep("_2", colnames(Table_2.1))) > 0) {
colnames(Table_2.1) <- gsub("%", "\\\\%", colnames(Table_2.1))
main_column_names <- colnames(Table_2.1)[!grepl("_2", colnames(Table_2.1))]
significance_column_names <- colnames(Table_2.1)[grepl("_sig", colnames(Table_2.1))]

Table_2.1 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.1 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.1) && length(grep("_2", colnames(Table_2.1))) > 0) {
comparison_column_names <- colnames(Table_2.1)[grepl("_2", colnames(Table_2.1))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.1 %>% select(tidyselect::all_of(colnames(Table_2.1)[!colnames(Table_2.1) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.2: Gender of all household members by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.2)) {
Table_2.2 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.2)) {
if (length(grep("_2", colnames(Table_2.2))) > 0) {
colnames(Table_2.2) <- gsub("%", "\\\\%", colnames(Table_2.2))
main_column_names <- colnames(Table_2.2)[!grepl("_2", colnames(Table_2.2))]
significance_column_names <- colnames(Table_2.2)[grepl("_sig", colnames(Table_2.2))]

Table_2.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.2 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.2) && length(grep("_2", colnames(Table_2.2))) > 0) {
comparison_column_names <- colnames(Table_2.2)[grepl("_2", colnames(Table_2.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.2 %>% select(tidyselect::all_of(colnames(Table_2.2)[!colnames(Table_2.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.3: All household members with a long-term physical or mental health condition by year
### Column percentages, Adults
### This question was changed in 2014, so this data is no longer comparable with previous years. Therefore, 2013 data is not presented here.
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.3)) {
Table_2.3 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.3)) {
if (length(grep("_2", colnames(Table_2.3))) > 0) {
colnames(Table_2.3) <- gsub("%", "\\\\%", colnames(Table_2.3))
main_column_names <- colnames(Table_2.3)[!grepl("_2", colnames(Table_2.3))]
significance_column_names <- colnames(Table_2.3)[grepl("_sig", colnames(Table_2.3))]

Table_2.3 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.3 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.3) && length(grep("_2", colnames(Table_2.3))) > 0) {
comparison_column_names <- colnames(Table_2.3)[grepl("_2", colnames(Table_2.3))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.3 %>% select(tidyselect::all_of(colnames(Table_2.3)[!colnames(Table_2.3) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 2.1: Age of adults by year
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_2.1)) {
Figure_2.1 %>%
kable("latex", escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.1)) {
if (length(grep("_2", colnames(Figure_2.1))) > 0) {
colnames(Figure_2.1) <- gsub("%", "\\\\%", colnames(Figure_2.1))
main_column_names <- colnames(Figure_2.1)[!grepl("_2", colnames(Figure_2.1))]
significance_column_names <- colnames(Figure_2.1)[grepl("_sig", colnames(Figure_2.1))]

Figure_2.1 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#00A3A3", `1999/2000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#00A3A3", `2001/2002_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#00A3A3", `2003/2004_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#00A3A3", `2005/2006_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#00A3A3", `2007/2008_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
Figure_2.1 %>%
kable("latex", escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.1) && length(grep("_2", colnames(Figure_2.1))) > 0) {
comparison_column_names <- colnames(Figure_2.1)[grepl("_2", colnames(Figure_2.1))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_2.1 %>% select(tidyselect::all_of(colnames(Figure_2.1)[!colnames(Figure_2.1) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#C3C3FF", `1999/2000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#C3C3FF", `2001/2002_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#C3C3FF", `2003/2004_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#C3C3FF", `2005/2006_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#C3C3FF", `2007/2008_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 2.2: Gender of adults by year
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_2.2)) {
Figure_2.2 %>%
kable("latex", escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.2)) {
if (length(grep("_2", colnames(Figure_2.2))) > 0) {
colnames(Figure_2.2) <- gsub("%", "\\\\%", colnames(Figure_2.2))
main_column_names <- colnames(Figure_2.2)[!grepl("_2", colnames(Figure_2.2))]
significance_column_names <- colnames(Figure_2.2)[grepl("_sig", colnames(Figure_2.2))]

Figure_2.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#00A3A3", `1999/2000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#00A3A3", `2001/2002_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#00A3A3", `2003/2004_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#00A3A3", `2005/2006_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#00A3A3", `2007/2008_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
Figure_2.2 %>%
kable("latex", escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.2) && length(grep("_2", colnames(Figure_2.2))) > 0) {
comparison_column_names <- colnames(Figure_2.2)[grepl("_2", colnames(Figure_2.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_2.2 %>% select(tidyselect::all_of(colnames(Figure_2.2)[!colnames(Figure_2.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#C3C3FF", `1999/2000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#C3C3FF", `2001/2002_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#C3C3FF", `2003/2004_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#C3C3FF", `2005/2006_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#C3C3FF", `2007/2008_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.4, Figure 2.3: Adults with a long-term physical or mental health condition by year
### Column percentages, Adults
### The question asked in its current form was introduced in 2012 and so not directly comparable with the previous years
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.4_Figure_2.3)) {
Table_2.4_Figure_2.3 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.4_Figure_2.3)) {
if (length(grep("_2", colnames(Table_2.4_Figure_2.3))) > 0) {
colnames(Table_2.4_Figure_2.3) <- gsub("%", "\\\\%", colnames(Table_2.4_Figure_2.3))
main_column_names <- colnames(Table_2.4_Figure_2.3)[!grepl("_2", colnames(Table_2.4_Figure_2.3))]
significance_column_names <- colnames(Table_2.4_Figure_2.3)[grepl("_sig", colnames(Table_2.4_Figure_2.3))]

Table_2.4_Figure_2.3 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.4_Figure_2.3 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.4_Figure_2.3) && length(grep("_2", colnames(Table_2.4_Figure_2.3))) > 0) {
comparison_column_names <- colnames(Table_2.4_Figure_2.3)[grepl("_2", colnames(Table_2.4_Figure_2.3))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.4_Figure_2.3 %>% select(tidyselect::all_of(colnames(Table_2.4_Figure_2.3)[!colnames(Table_2.4_Figure_2.3) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.5: Ethnicity of adults by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.5)) {
Table_2.5 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.5)) {
if (length(grep("_2", colnames(Table_2.5))) > 0) {
colnames(Table_2.5) <- gsub("%", "\\\\%", colnames(Table_2.5))
main_column_names <- colnames(Table_2.5)[!grepl("_2", colnames(Table_2.5))]
significance_column_names <- colnames(Table_2.5)[grepl("_sig", colnames(Table_2.5))]

Table_2.5 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.5 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.5) && length(grep("_2", colnames(Table_2.5))) > 0) {
comparison_column_names <- colnames(Table_2.5)[grepl("_2", colnames(Table_2.5))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.5 %>% select(tidyselect::all_of(colnames(Table_2.5)[!colnames(Table_2.5) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.6: Economic status of all adults aged 16-64
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_2.6)) {
Table_2.6 %>%
kable("latex", escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_2.6)) {
if (length(grep("_2", colnames(Table_2.6))) > 0) {
colnames(Table_2.6) <- gsub("%", "\\\\%", colnames(Table_2.6))
main_column_names <- colnames(Table_2.6)[!grepl("_2", colnames(Table_2.6))]
significance_column_names <- colnames(Table_2.6)[grepl("_sig", colnames(Table_2.6))]

Table_2.6 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`All adults` = cell_spec(`All adults`, "latex", background = case_when(`All adults_sig` == "HIGHER" ~ "#00A3A3", `All adults_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Adults aged 16 to 64` = cell_spec(`Adults aged 16 to 64`, "latex", background = case_when(`Adults aged 16 to 64_sig` == "HIGHER" ~ "#00A3A3", `Adults aged 16 to 64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
Table_2.6 %>%
kable("latex", escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_2.6) && length(grep("_2", colnames(Table_2.6))) > 0) {
comparison_column_names <- colnames(Table_2.6)[grepl("_2", colnames(Table_2.6))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.6 %>% select(tidyselect::all_of(colnames(Table_2.6)[!colnames(Table_2.6) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`All adults` = cell_spec(`All adults`, "latex", background = case_when(`All adults_sig` == "HIGHER" ~ "#C3C3FF", `All adults_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Adults aged 16 to 64` = cell_spec(`Adults aged 16 to 64`, "latex", background = case_when(`Adults aged 16 to 64_sig` == "HIGHER" ~ "#C3C3FF", `Adults aged 16 to 64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 2.4: Economic status of adults by year - selected groups
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_2.4)) {
Figure_2.4 %>%
kable("latex", escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down") %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.4)) {
if (length(grep("_2", colnames(Figure_2.4))) > 0) {
colnames(Figure_2.4) <- gsub("%", "\\\\%", colnames(Figure_2.4))
main_column_names <- colnames(Figure_2.4)[!grepl("_2", colnames(Figure_2.4))]
significance_column_names <- colnames(Figure_2.4)[grepl("_sig", colnames(Figure_2.4))]

Figure_2.4 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#00A3A3", `1999/2000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#00A3A3", `2001/2002_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#00A3A3", `2003/2004_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#00A3A3", `2005/2006_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#00A3A3", `2007/2008_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em") %>% kable_styling(latex_options = "scale_down")
} else {
Figure_2.4 %>%
kable("latex", escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em") %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.4) && length(grep("_2", colnames(Figure_2.4))) > 0) {
comparison_column_names <- colnames(Figure_2.4)[grepl("_2", colnames(Figure_2.4))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_2.4 %>% select(tidyselect::all_of(colnames(Figure_2.4)[!colnames(Figure_2.4) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#C3C3FF", `1999/2000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#C3C3FF", `2001/2002_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#C3C3FF", `2003/2004_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#C3C3FF", `2005/2006_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#C3C3FF", `2007/2008_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em") %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.7: Sexual orientation of adults by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.7)) {
Table_2.7 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.7)) {
if (length(grep("_2", colnames(Table_2.7))) > 0) {
colnames(Table_2.7) <- gsub("%", "\\\\%", colnames(Table_2.7))
main_column_names <- colnames(Table_2.7)[!grepl("_2", colnames(Table_2.7))]
significance_column_names <- colnames(Table_2.7)[grepl("_sig", colnames(Table_2.7))]

Table_2.7 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.7 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.7) && length(grep("_2", colnames(Table_2.7))) > 0) {
comparison_column_names <- colnames(Table_2.7)[grepl("_2", colnames(Table_2.7))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.7 %>% select(tidyselect::all_of(colnames(Table_2.7)[!colnames(Table_2.7) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 2.5: Religious belonging of adults by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_2.5)) {
Figure_2.5 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.5)) {
if (length(grep("_2", colnames(Figure_2.5))) > 0) {
colnames(Figure_2.5) <- gsub("%", "\\\\%", colnames(Figure_2.5))
main_column_names <- colnames(Figure_2.5)[!grepl("_2", colnames(Figure_2.5))]
significance_column_names <- colnames(Figure_2.5)[grepl("_sig", colnames(Figure_2.5))]

Figure_2.5 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Figure_2.5 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_2.5) && length(grep("_2", colnames(Figure_2.5))) > 0) {
comparison_column_names <- colnames(Figure_2.5)[grepl("_2", colnames(Figure_2.5))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_2.5 %>% select(tidyselect::all_of(colnames(Figure_2.5)[!colnames(Figure_2.5) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.8: Marital status of adults by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.8)) {
Table_2.8 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.8)) {
if (length(grep("_2", colnames(Table_2.8))) > 0) {
colnames(Table_2.8) <- gsub("%", "\\\\%", colnames(Table_2.8))
main_column_names <- colnames(Table_2.8)[!grepl("_2", colnames(Table_2.8))]
significance_column_names <- colnames(Table_2.8)[grepl("_sig", colnames(Table_2.8))]

Table_2.8 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.8 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.8) && length(grep("_2", colnames(Table_2.8))) > 0) {
comparison_column_names <- colnames(Table_2.8)[grepl("_2", colnames(Table_2.8))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.8 %>% select(tidyselect::all_of(colnames(Table_2.8)[!colnames(Table_2.8) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.9: Current marital status of adults by age
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_2.9)) {
Table_2.9 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_2.9)) {
if (length(grep("_2", colnames(Table_2.9))) > 0) {
colnames(Table_2.9) <- gsub("%", "\\\\%", colnames(Table_2.9))
main_column_names <- colnames(Table_2.9)[!grepl("_2", colnames(Table_2.9))]
significance_column_names <- colnames(Table_2.9)[grepl("_sig", colnames(Table_2.9))]

Table_2.9 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`16-24` = cell_spec(`16-24`, "latex", background = case_when(`16-24_sig` == "HIGHER" ~ "#00A3A3", `16-24_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`25-34` = cell_spec(`25-34`, "latex", background = case_when(`25-34_sig` == "HIGHER" ~ "#00A3A3", `25-34_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`35 - 44` = cell_spec(`35 - 44`, "latex", background = case_when(`35 - 44_sig` == "HIGHER" ~ "#00A3A3", `35 - 44_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`45-59` = cell_spec(`45-59`, "latex", background = case_when(`45-59_sig` == "HIGHER" ~ "#00A3A3", `45-59_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`60-74` = cell_spec(`60-74`, "latex", background = case_when(`60-74_sig` == "HIGHER" ~ "#00A3A3", `60-74_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`75+` = cell_spec(`75+`, "latex", background = case_when(`75+_sig` == "HIGHER" ~ "#00A3A3", `75+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.9 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_2.9) && length(grep("_2", colnames(Table_2.9))) > 0) {
comparison_column_names <- colnames(Table_2.9)[grepl("_2", colnames(Table_2.9))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.9 %>% select(tidyselect::all_of(colnames(Table_2.9)[!colnames(Table_2.9) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`16-24` = cell_spec(`16-24`, "latex", background = case_when(`16-24_sig` == "HIGHER" ~ "#C3C3FF", `16-24_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`25-34` = cell_spec(`25-34`, "latex", background = case_when(`25-34_sig` == "HIGHER" ~ "#C3C3FF", `25-34_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`35 - 44` = cell_spec(`35 - 44`, "latex", background = case_when(`35 - 44_sig` == "HIGHER" ~ "#C3C3FF", `35 - 44_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`45-59` = cell_spec(`45-59`, "latex", background = case_when(`45-59_sig` == "HIGHER" ~ "#C3C3FF", `45-59_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`60-74` = cell_spec(`60-74`, "latex", background = case_when(`60-74_sig` == "HIGHER" ~ "#C3C3FF", `60-74_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`75+` = cell_spec(`75+`, "latex", background = case_when(`75+_sig` == "HIGHER" ~ "#C3C3FF", `75+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.10: Age of adults by marital status
### Row percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_2.10)) {
Table_2.10 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_2.10)) {
if (length(grep("_2", colnames(Table_2.10))) > 0) {
colnames(Table_2.10) <- gsub("%", "\\\\%", colnames(Table_2.10))
main_column_names <- colnames(Table_2.10)[!grepl("_2", colnames(Table_2.10))]
significance_column_names <- colnames(Table_2.10)[grepl("_sig", colnames(Table_2.10))]

Table_2.10 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`16-24` = cell_spec(`16-24`, "latex", background = case_when(`16-24_sig` == "HIGHER" ~ "#00A3A3", `16-24_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`25-34` = cell_spec(`25-34`, "latex", background = case_when(`25-34_sig` == "HIGHER" ~ "#00A3A3", `25-34_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`35 - 44` = cell_spec(`35 - 44`, "latex", background = case_when(`35 - 44_sig` == "HIGHER" ~ "#00A3A3", `35 - 44_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`45-59` = cell_spec(`45-59`, "latex", background = case_when(`45-59_sig` == "HIGHER" ~ "#00A3A3", `45-59_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`60-74` = cell_spec(`60-74`, "latex", background = case_when(`60-74_sig` == "HIGHER" ~ "#00A3A3", `60-74_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`75+` = cell_spec(`75+`, "latex", background = case_when(`75+_sig` == "HIGHER" ~ "#00A3A3", `75+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.10 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_2.10) && length(grep("_2", colnames(Table_2.10))) > 0) {
comparison_column_names <- colnames(Table_2.10)[grepl("_2", colnames(Table_2.10))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.10 %>% select(tidyselect::all_of(colnames(Table_2.10)[!colnames(Table_2.10) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`16-24` = cell_spec(`16-24`, "latex", background = case_when(`16-24_sig` == "HIGHER" ~ "#C3C3FF", `16-24_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`25-34` = cell_spec(`25-34`, "latex", background = case_when(`25-34_sig` == "HIGHER" ~ "#C3C3FF", `25-34_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`35 - 44` = cell_spec(`35 - 44`, "latex", background = case_when(`35 - 44_sig` == "HIGHER" ~ "#C3C3FF", `35 - 44_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`45-59` = cell_spec(`45-59`, "latex", background = case_when(`45-59_sig` == "HIGHER" ~ "#C3C3FF", `45-59_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`60-74` = cell_spec(`60-74`, "latex", background = case_when(`60-74_sig` == "HIGHER" ~ "#C3C3FF", `60-74_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`75+` = cell_spec(`75+`, "latex", background = case_when(`75+_sig` == "HIGHER" ~ "#C3C3FF", `75+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.11: Household type of households by year
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.11)) {
Table_2.11 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.11)) {
if (length(grep("_2", colnames(Table_2.11))) > 0) {
colnames(Table_2.11) <- gsub("%", "\\\\%", colnames(Table_2.11))
main_column_names <- colnames(Table_2.11)[!grepl("_2", colnames(Table_2.11))]
significance_column_names <- colnames(Table_2.11)[grepl("_sig", colnames(Table_2.11))]

Table_2.11 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.11 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.11) && length(grep("_2", colnames(Table_2.11))) > 0) {
comparison_column_names <- colnames(Table_2.11)[grepl("_2", colnames(Table_2.11))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.11 %>% select(tidyselect::all_of(colnames(Table_2.11)[!colnames(Table_2.11) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.12: Households with children by year
### Column percentages, Households

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.12)) {
Table_2.12 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.12)) {
if (length(grep("_2", colnames(Table_2.12))) > 0) {
colnames(Table_2.12) <- gsub("%", "\\\\%", colnames(Table_2.12))
main_column_names <- colnames(Table_2.12)[!grepl("_2", colnames(Table_2.12))]
significance_column_names <- colnames(Table_2.12)[grepl("_sig", colnames(Table_2.12))]

Table_2.12 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.12 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.12) && length(grep("_2", colnames(Table_2.12))) > 0) {
comparison_column_names <- colnames(Table_2.12)[grepl("_2", colnames(Table_2.12))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.12 %>% select(tidyselect::all_of(colnames(Table_2.12)[!colnames(Table_2.12) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.13: Property type of households by year
### Column percentages, Households

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.13)) {
Table_2.13 %>%
kable("latex", escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.13)) {
if (length(grep("_2", colnames(Table_2.13))) > 0) {
colnames(Table_2.13) <- gsub("%", "\\\\%", colnames(Table_2.13))
main_column_names <- colnames(Table_2.13)[!grepl("_2", colnames(Table_2.13))]
significance_column_names <- colnames(Table_2.13)[grepl("_sig", colnames(Table_2.13))]

Table_2.13 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
Table_2.13 %>%
kable("latex", escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.13) && length(grep("_2", colnames(Table_2.13))) > 0) {
comparison_column_names <- colnames(Table_2.13)[grepl("_2", colnames(Table_2.13))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.13 %>% select(tidyselect::all_of(colnames(Table_2.13)[!colnames(Table_2.13) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.14: Tenure of households by year
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.14)) {
Table_2.14 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.14)) {
if (length(grep("_2", colnames(Table_2.14))) > 0) {
colnames(Table_2.14) <- gsub("%", "\\\\%", colnames(Table_2.14))
main_column_names <- colnames(Table_2.14)[!grepl("_2", colnames(Table_2.14))]
significance_column_names <- colnames(Table_2.14)[grepl("_sig", colnames(Table_2.14))]

Table_2.14 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.14 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.14) && length(grep("_2", colnames(Table_2.14))) > 0) {
comparison_column_names <- colnames(Table_2.14)[grepl("_2", colnames(Table_2.14))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.14 %>% select(tidyselect::all_of(colnames(Table_2.14)[!colnames(Table_2.14) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.15: Scottish Index of Multiple Deprivation of households by year
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.15)) {
Table_2.15 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.15)) {
if (length(grep("_2", colnames(Table_2.15))) > 0) {
colnames(Table_2.15) <- gsub("%", "\\\\%", colnames(Table_2.15))
main_column_names <- colnames(Table_2.15)[!grepl("_2", colnames(Table_2.15))]
significance_column_names <- colnames(Table_2.15)[grepl("_sig", colnames(Table_2.15))]

Table_2.15 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.15 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.15) && length(grep("_2", colnames(Table_2.15))) > 0) {
comparison_column_names <- colnames(Table_2.15)[grepl("_2", colnames(Table_2.15))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.15 %>% select(tidyselect::all_of(colnames(Table_2.15)[!colnames(Table_2.15) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.16: Urban rural split of households by year
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.16)) {
Table_2.16 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.16)) {
if (length(grep("_2", colnames(Table_2.16))) > 0) {
colnames(Table_2.16) <- gsub("%", "\\\\%", colnames(Table_2.16))
main_column_names <- colnames(Table_2.16)[!grepl("_2", colnames(Table_2.16))]
significance_column_names <- colnames(Table_2.16)[grepl("_sig", colnames(Table_2.16))]

Table_2.16 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.16 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.16) && length(grep("_2", colnames(Table_2.16))) > 0) {
comparison_column_names <- colnames(Table_2.16)[grepl("_2", colnames(Table_2.16))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.16 %>% select(tidyselect::all_of(colnames(Table_2.16)[!colnames(Table_2.16) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 2.17: Household income of households by year
### Column percentages, Households

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_2.17)) {
Table_2.17 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.17)) {
if (length(grep("_2", colnames(Table_2.17))) > 0) {
colnames(Table_2.17) <- gsub("%", "\\\\%", colnames(Table_2.17))
main_column_names <- colnames(Table_2.17)[!grepl("_2", colnames(Table_2.17))]
significance_column_names <- colnames(Table_2.17)[grepl("_sig", colnames(Table_2.17))]

Table_2.17 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_2.17 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_2.17) && length(grep("_2", colnames(Table_2.17))) > 0) {
comparison_column_names <- colnames(Table_2.17)[grepl("_2", colnames(Table_2.17))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_2.17 %>% select(tidyselect::all_of(colnames(Table_2.17)[!colnames(Table_2.17) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
