---
params:
  report_title: ""
  author: ""
  date: ""
  local_authority: ""
  year: ""
  topic_data: ""
  comparison_type: ""
  comparator: ""
title: "`r params$report_title`"
author: "`r params$author`"
date: "`r params$date`"
output:
  pdf_document:
    toc: yes
    fig_caption: false
header-includes:
    - \hypersetup{colorlinks=true, linkcolor = black, urlcolor = [RGB]{0, 163, 163}}
    - \usepackage{titling}
    - \pretitle{\begin{center}
      \includegraphics[width=2in,height=2in]{../www/new_logo.png}\LARGE\\}
    - \posttitle{\end{center}}
    - \renewcommand{\familydefault}{\sfdefault}
classoption: landscape
fontsize: 10pt
papersize: a4
geometry: margin=1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
options(tinytex.verbose = TRUE)

library(knitr)
library(dplyr)
library(kableExtra)
library(png)
library(tidyselect)

local_authority <- params$local_authority
year <- params$year
topic_data <- params$topic_data
comparison_type <- params$comparison_type
comparator <- params$comparator


Table_5.1_Figure_5.1 <- topic_data[[1]]

Table_5.2 <- topic_data[[2]]

Table_5.3_Figure_5.2 <- topic_data[[3]]

Figure_5.3 <- topic_data[[4]]

Figure_5.4 <- topic_data[[5]]

Figure_5.5 <- topic_data[[6]]

Figure_5.6 <- topic_data[[7]]

Table_5.4 <- topic_data[[8]]

Table_5.5 <- topic_data[[9]]

Figure_5.7 <- topic_data[[10]]

Figure_5.8 <- topic_data[[11]]


main_table_title <- paste0(local_authority, ", ", year)

eval_comparison <- ifelse(comparison_type == "No comparison", FALSE, TRUE)

eval_comparison_time_series <- ifelse(comparison_type == "Year" | comparison_type == "No comparison", FALSE, TRUE)

comparison_table_title <- if (comparison_type == "Local Authority") {
  paste0(comparator, ", ", year)
} else if (comparison_type == "Year") {
  paste0(local_authority, ", ", comparator)
} else {
  NULL
  }

```

## Acknowledgements
The Scottish Government acknowledges and thanks the 10,530
people across Scotland who gave their time to take part in the
Scottish Household Survey 2018.
This report was produced by the Scottish Household Survey Project Team
at the Scottish Government.
We would also like to thank all the Scottish Government lead analysts who
contributed to the project.
Finally, special thanks to Ipsos MORI and their interviewers for continuous
and relentless efforts during the fieldwork.

## Key

```{=latex}
$ \color[RGB]{0, 163, 163} \blacksquare $ Significantly higher $ \color[RGB]{195, 195, 255} \blacksquare $ Significantly lower
```
\pagebreak

## Table 5.1, Figure 5.1: Highest level of qualifications held by adults aged 16 and over by year, 2007-2018
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

### `r local_authority`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Table_5.1_Figure_5.1)) {
Table_5.1_Figure_5.1 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.1_Figure_5.1)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_5.1_Figure_5.1)) {
if (length(grep("_2", colnames(Table_5.1_Figure_5.1))) > 0) {
colnames(Table_5.1_Figure_5.1) <- gsub("%", "\\\\%", colnames(Table_5.1_Figure_5.1))
main_column_names <- colnames(Table_5.1_Figure_5.1)[!grepl("_2", colnames(Table_5.1_Figure_5.1))]
significance_column_names <- colnames(Table_5.1_Figure_5.1)[grepl("_sig", colnames(Table_5.1_Figure_5.1))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_5.1_Figure_5.1 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#00A3A3", `2007/2008_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_5.1_Figure_5.1 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.1_Figure_5.1)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison_time_series}

asis_output(paste0("### ", comparator))
  
```

```{r eval=eval_comparison_time_series}
if (!is.null(Table_5.1_Figure_5.1) && length(grep("_2", colnames(Table_5.1_Figure_5.1))) > 0) {
comparison_column_names <- colnames(Table_5.1_Figure_5.1)[grepl("_2", colnames(Table_5.1_Figure_5.1))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_5.1_Figure_5.1 %>% select(tidyselect::all_of(colnames(Table_5.1_Figure_5.1)[!colnames(Table_5.1_Figure_5.1) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#C3C3FF", `2007/2008_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 5.2: Highest level of qualification held by gender and age of adults aged 16 and over
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_5.2)) {
Table_5.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.2)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_5.2)) {
if (length(grep("_2", colnames(Table_5.2))) > 0) {
colnames(Table_5.2) <- gsub("%", "\\\\%", colnames(Table_5.2))
main_column_names <- colnames(Table_5.2)[!grepl("_2", colnames(Table_5.2))]
significance_column_names <- colnames(Table_5.2)[grepl("_sig", colnames(Table_5.2))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_5.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-59` = cell_spec(`40-59`, "latex", background = case_when(`40-59_sig` == "HIGHER" ~ "#00A3A3", `40-59_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`60 plus` = cell_spec(`60 plus`, "latex", background = case_when(`60 plus_sig` == "HIGHER" ~ "#00A3A3", `60 plus_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_5.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.2)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Table_5.2) && length(grep("_2", colnames(Table_5.2))) > 0) {
comparison_column_names <- colnames(Table_5.2)[grepl("_2", colnames(Table_5.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_5.2 %>% select(tidyselect::all_of(colnames(Table_5.2)[!colnames(Table_5.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-59` = cell_spec(`40-59`, "latex", background = case_when(`40-59_sig` == "HIGHER" ~ "#C3C3FF", `40-59_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`60 plus` = cell_spec(`60 plus`, "latex", background = case_when(`60 plus_sig` == "HIGHER" ~ "#C3C3FF", `60 plus_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 5.3, Figure 5.2: Highest level of qualification held by adults aged 16-64 by net annual household income
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_5.3_Figure_5.2)) {
Table_5.3_Figure_5.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.3_Figure_5.2)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_5.3_Figure_5.2)) {
if (length(grep("_2", colnames(Table_5.3_Figure_5.2))) > 0) {
colnames(Table_5.3_Figure_5.2) <- gsub("%", "\\\\%", colnames(Table_5.3_Figure_5.2))
main_column_names <- colnames(Table_5.3_Figure_5.2)[!grepl("_2", colnames(Table_5.3_Figure_5.2))]
significance_column_names <- colnames(Table_5.3_Figure_5.2)[grepl("_sig", colnames(Table_5.3_Figure_5.2))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_5.3_Figure_5.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Up to £15,000` = cell_spec(`Up to £15,000`, "latex", background = case_when(`Up to £15,000_sig` == "HIGHER" ~ "#00A3A3", `Up to £15,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`£15,001 to £30,000` = cell_spec(`£15,001 to £30,000`, "latex", background = case_when(`£15,001 to £30,000_sig` == "HIGHER" ~ "#00A3A3", `£15,001 to £30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Over £30,000` = cell_spec(`Over £30,000`, "latex", background = case_when(`Over £30,000_sig` == "HIGHER" ~ "#00A3A3", `Over £30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Table_5.3_Figure_5.2 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.3_Figure_5.2)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Table_5.3_Figure_5.2) && length(grep("_2", colnames(Table_5.3_Figure_5.2))) > 0) {
comparison_column_names <- colnames(Table_5.3_Figure_5.2)[grepl("_2", colnames(Table_5.3_Figure_5.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_5.3_Figure_5.2 %>% select(tidyselect::all_of(colnames(Table_5.3_Figure_5.2)[!colnames(Table_5.3_Figure_5.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Up to £15,000` = cell_spec(`Up to £15,000`, "latex", background = case_when(`Up to £15,000_sig` == "HIGHER" ~ "#C3C3FF", `Up to £15,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`£15,001 to £30,000` = cell_spec(`£15,001 to £30,000`, "latex", background = case_when(`£15,001 to £30,000_sig` == "HIGHER" ~ "#C3C3FF", `£15,001 to £30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Over £30,000` = cell_spec(`Over £30,000`, "latex", background = case_when(`Over £30,000_sig` == "HIGHER" ~ "#C3C3FF", `Over £30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 5.3: Current economic situation of adults aged 16 and over
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_5.3)) {
Figure_5.3 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.3)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.3)) {
if (length(grep("_2", colnames(Figure_5.3))) > 0) {
colnames(Figure_5.3) <- gsub("%", "\\\\%", colnames(Figure_5.3))
main_column_names <- colnames(Figure_5.3)[!grepl("_2", colnames(Figure_5.3))]
significance_column_names <- colnames(Figure_5.3)[grepl("_sig", colnames(Figure_5.3))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_5.3 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_5.3 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.3)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.3) && length(grep("_2", colnames(Figure_5.3))) > 0) {
comparison_column_names <- colnames(Figure_5.3)[grepl("_2", colnames(Figure_5.3))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_5.3 %>% select(tidyselect::all_of(colnames(Figure_5.3)[!colnames(Figure_5.3) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 5.4: Adults aged 16 and over in work over time, 1999-2018
### Column percentages, Adults

### `r local_authority`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_5.4)) {
Figure_5.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.4)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_5.4)) {
if (length(grep("_2", colnames(Figure_5.4))) > 0) {
colnames(Figure_5.4) <- gsub("%", "\\\\%", colnames(Figure_5.4))
main_column_names <- colnames(Figure_5.4)[!grepl("_2", colnames(Figure_5.4))]
significance_column_names <- colnames(Figure_5.4)[grepl("_sig", colnames(Figure_5.4))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_5.4 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#00A3A3", `1999/2000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#00A3A3", `2001/2002_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#00A3A3", `2003/2004_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#00A3A3", `2005/2006_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#00A3A3", `2007/2008_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
Figure_5.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.4)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison_time_series}

asis_output(paste0("### ", comparator))
  
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_5.4) && length(grep("_2", colnames(Figure_5.4))) > 0) {
comparison_column_names <- colnames(Figure_5.4)[grepl("_2", colnames(Figure_5.4))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_5.4 %>% select(tidyselect::all_of(colnames(Figure_5.4)[!colnames(Figure_5.4) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#C3C3FF", `1999/2000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#C3C3FF", `2001/2002_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#C3C3FF", `2003/2004_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#C3C3FF", `2005/2006_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#C3C3FF", `2007/2008_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 5.5: Current economic situation of adults aged 16-64 over time, 1999-2018
### Column percentages, Adults

### `r local_authority`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_5.5)) {
Figure_5.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.5)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_5.5)) {
if (length(grep("_2", colnames(Figure_5.5))) > 0) {
colnames(Figure_5.5) <- gsub("%", "\\\\%", colnames(Figure_5.5))
main_column_names <- colnames(Figure_5.5)[!grepl("_2", colnames(Figure_5.5))]
significance_column_names <- colnames(Figure_5.5)[grepl("_sig", colnames(Figure_5.5))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_5.5 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#00A3A3", `1999/2000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#00A3A3", `2001/2002_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#00A3A3", `2003/2004_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#00A3A3", `2005/2006_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#00A3A3", `2007/2008_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
Figure_5.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.5)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison_time_series}

asis_output(paste0("### ", comparator))
  
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_5.5) && length(grep("_2", colnames(Figure_5.5))) > 0) {
comparison_column_names <- colnames(Figure_5.5)[grepl("_2", colnames(Figure_5.5))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_5.5 %>% select(tidyselect::all_of(colnames(Figure_5.5)[!colnames(Figure_5.5) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#C3C3FF", `1999/2000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#C3C3FF", `2001/2002_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#C3C3FF", `2003/2004_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#C3C3FF", `2005/2006_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#C3C3FF", `2007/2008_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 5.6: Current economic situation of adults aged 16-64 by gender
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_5.6)) {
Figure_5.6 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.6)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.6)) {
if (length(grep("_2", colnames(Figure_5.6))) > 0) {
colnames(Figure_5.6) <- gsub("%", "\\\\%", colnames(Figure_5.6))
main_column_names <- colnames(Figure_5.6)[!grepl("_2", colnames(Figure_5.6))]
significance_column_names <- colnames(Figure_5.6)[grepl("_sig", colnames(Figure_5.6))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_5.6 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#00A3A3", `Man / Boy_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#00A3A3", `Woman / Girl_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#00A3A3", `Identified in another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_5.6 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.6)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.6) && length(grep("_2", colnames(Figure_5.6))) > 0) {
comparison_column_names <- colnames(Figure_5.6)[grepl("_2", colnames(Figure_5.6))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_5.6 %>% select(tidyselect::all_of(colnames(Figure_5.6)[!colnames(Figure_5.6) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Man / Boy` = cell_spec(`Man / Boy`, "latex", background = case_when(`Man / Boy_sig` == "HIGHER" ~ "#C3C3FF", `Man / Boy_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Woman / Girl` = cell_spec(`Woman / Girl`, "latex", background = case_when(`Woman / Girl_sig` == "HIGHER" ~ "#C3C3FF", `Woman / Girl_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Identified in another way` = cell_spec(`Identified in another way`, "latex", background = case_when(`Identified in another way_sig` == "HIGHER" ~ "#C3C3FF", `Identified in another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 5.4: Current economic situation of adults aged 16-64 by highest level of qualification
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_5.4)) {
Table_5.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.4)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_5.4)) {
if (length(grep("_2", colnames(Table_5.4))) > 0) {
colnames(Table_5.4) <- gsub("%", "\\\\%", colnames(Table_5.4))
main_column_names <- colnames(Table_5.4)[!grepl("_2", colnames(Table_5.4))]
significance_column_names <- colnames(Table_5.4)[grepl("_sig", colnames(Table_5.4))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_5.4 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Degree/professional qualification` = cell_spec(`Degree/professional qualification`, "latex", background = case_when(`Degree/professional qualification_sig` == "HIGHER" ~ "#00A3A3", `Degree/professional qualification_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Higher/A level/O Grade/Standard Grade` = cell_spec(`Higher/A level/O Grade/Standard Grade`, "latex", background = case_when(`Higher/A level/O Grade/Standard Grade_sig` == "HIGHER" ~ "#00A3A3", `Higher/A level/O Grade/Standard Grade_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Other qualification` = cell_spec(`Other qualification`, "latex", background = case_when(`Other qualification_sig` == "HIGHER" ~ "#00A3A3", `Other qualification_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`No qualifications` = cell_spec(`No qualifications`, "latex", background = case_when(`No qualifications_sig` == "HIGHER" ~ "#00A3A3", `No qualifications_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Qualifications not known` = cell_spec(`Qualifications not known`, "latex", background = case_when(`Qualifications not known_sig` == "HIGHER" ~ "#00A3A3", `Qualifications not known_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
Table_5.4 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.4)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Table_5.4) && length(grep("_2", colnames(Table_5.4))) > 0) {
comparison_column_names <- colnames(Table_5.4)[grepl("_2", colnames(Table_5.4))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_5.4 %>% select(tidyselect::all_of(colnames(Table_5.4)[!colnames(Table_5.4) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Degree/professional qualification` = cell_spec(`Degree/professional qualification`, "latex", background = case_when(`Degree/professional qualification_sig` == "HIGHER" ~ "#C3C3FF", `Degree/professional qualification_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Higher/A level/O Grade/Standard Grade` = cell_spec(`Higher/A level/O Grade/Standard Grade`, "latex", background = case_when(`Higher/A level/O Grade/Standard Grade_sig` == "HIGHER" ~ "#C3C3FF", `Higher/A level/O Grade/Standard Grade_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Other qualification` = cell_spec(`Other qualification`, "latex", background = case_when(`Other qualification_sig` == "HIGHER" ~ "#C3C3FF", `Other qualification_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`No qualifications` = cell_spec(`No qualifications`, "latex", background = case_when(`No qualifications_sig` == "HIGHER" ~ "#C3C3FF", `No qualifications_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Qualifications not known` = cell_spec(`Qualifications not known`, "latex", background = case_when(`Qualifications not known_sig` == "HIGHER" ~ "#C3C3FF", `Qualifications not known_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Table 5.5: Current economic situation of adults aged 16-64 by long-standing limiting illness, health problem or disability
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_5.5)) {
Table_5.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.5)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_5.5)) {
if (length(grep("_2", colnames(Table_5.5))) > 0) {
colnames(Table_5.5) <- gsub("%", "\\\\%", colnames(Table_5.5))
main_column_names <- colnames(Table_5.5)[!grepl("_2", colnames(Table_5.5))]
significance_column_names <- colnames(Table_5.5)[grepl("_sig", colnames(Table_5.5))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Table_5.5 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Yes long-term condition` = cell_spec(`Yes long-term condition`, "latex", background = case_when(`Yes long-term condition_sig` == "HIGHER" ~ "#00A3A3", `Yes long-term condition_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`No long-term condition` = cell_spec(`No long-term condition`, "latex", background = case_when(`No long-term condition_sig` == "HIGHER" ~ "#00A3A3", `No long-term condition_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`All (including permanently sick or disabled)` = cell_spec(`All (including permanently sick or disabled)`, "latex", background = case_when(`All (including permanently sick or disabled)_sig` == "HIGHER" ~ "#00A3A3", `All (including permanently sick or disabled)_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Yes ('excluding permanently sick or disabled')` = cell_spec(`Yes ('excluding permanently sick or disabled')`, "latex", background = case_when(`Yes ('excluding permanently sick or disabled')_sig` == "HIGHER" ~ "#00A3A3", `Yes ('excluding permanently sick or disabled')_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`No ('excluding permanently sick or disabled')` = cell_spec(`No ('excluding permanently sick or disabled')`, "latex", background = case_when(`No ('excluding permanently sick or disabled')_sig` == "HIGHER" ~ "#00A3A3", `No ('excluding permanently sick or disabled')_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`All (excluding permanently sick or disabled)` = cell_spec(`All (excluding permanently sick or disabled)`, "latex", background = case_when(`All (excluding permanently sick or disabled)_sig` == "HIGHER" ~ "#00A3A3", `All (excluding permanently sick or disabled)_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
Table_5.5 %>%
kable("latex", col.names = gsub("blank", "", colnames(Table_5.5)), escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Table_5.5) && length(grep("_2", colnames(Table_5.5))) > 0) {
comparison_column_names <- colnames(Table_5.5)[grepl("_2", colnames(Table_5.5))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_5.5 %>% select(tidyselect::all_of(colnames(Table_5.5)[!colnames(Table_5.5) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Yes long-term condition` = cell_spec(`Yes long-term condition`, "latex", background = case_when(`Yes long-term condition_sig` == "HIGHER" ~ "#C3C3FF", `Yes long-term condition_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`No long-term condition` = cell_spec(`No long-term condition`, "latex", background = case_when(`No long-term condition_sig` == "HIGHER" ~ "#C3C3FF", `No long-term condition_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`All (including permanently sick or disabled)` = cell_spec(`All (including permanently sick or disabled)`, "latex", background = case_when(`All (including permanently sick or disabled)_sig` == "HIGHER" ~ "#C3C3FF", `All (including permanently sick or disabled)_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Yes ('excluding permanently sick or disabled')` = cell_spec(`Yes ('excluding permanently sick or disabled')`, "latex", background = case_when(`Yes ('excluding permanently sick or disabled')_sig` == "HIGHER" ~ "#C3C3FF", `Yes ('excluding permanently sick or disabled')_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`No ('excluding permanently sick or disabled')` = cell_spec(`No ('excluding permanently sick or disabled')`, "latex", background = case_when(`No ('excluding permanently sick or disabled')_sig` == "HIGHER" ~ "#C3C3FF", `No ('excluding permanently sick or disabled')_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`All (excluding permanently sick or disabled)` = cell_spec(`All (excluding permanently sick or disabled)`, "latex", background = case_when(`All (excluding permanently sick or disabled)_sig` == "HIGHER" ~ "#C3C3FF", `All (excluding permanently sick or disabled)_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T) %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 5.7: Number of adults aged 16 or over in paid employment by Scottish Index of Multiple Deprivation
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_5.7)) {
Figure_5.7 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.7)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.7)) {
if (length(grep("_2", colnames(Figure_5.7))) > 0) {
colnames(Figure_5.7) <- gsub("%", "\\\\%", colnames(Figure_5.7))
main_column_names <- colnames(Figure_5.7)[!grepl("_2", colnames(Figure_5.7))]
significance_column_names <- colnames(Figure_5.7)[grepl("_sig", colnames(Figure_5.7))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_5.7 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1 - 20\\% most deprived` = cell_spec(`1 - 20\\% most deprived`, "latex", background = case_when(`1 - 20\\% most deprived_sig` == "HIGHER" ~ "#00A3A3", `1 - 20\\% most deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#00A3A3", `2_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#00A3A3", `3_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#00A3A3", `4_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`5 - 20\\% least deprived` = cell_spec(`5 - 20\\% least deprived`, "latex", background = case_when(`5 - 20\\% least deprived_sig` == "HIGHER" ~ "#00A3A3", `5 - 20\\% least deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_5.7 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.7)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.7) && length(grep("_2", colnames(Figure_5.7))) > 0) {
comparison_column_names <- colnames(Figure_5.7)[grepl("_2", colnames(Figure_5.7))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_5.7 %>% select(tidyselect::all_of(colnames(Figure_5.7)[!colnames(Figure_5.7) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1 - 20\\% most deprived` = cell_spec(`1 - 20\\% most deprived`, "latex", background = case_when(`1 - 20\\% most deprived_sig` == "HIGHER" ~ "#C3C3FF", `1 - 20\\% most deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#C3C3FF", `2_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#C3C3FF", `3_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#C3C3FF", `4_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`5 - 20\\% least deprived` = cell_spec(`5 - 20\\% least deprived`, "latex", background = case_when(`5 - 20\\% least deprived_sig` == "HIGHER" ~ "#C3C3FF", `5 - 20\\% least deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

## Figure 5.8: Current economic situation of women aged 16-64 by the presence of children in the household
### Column percentages, Adults

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_5.8)) {
Figure_5.8 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.8)), escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.8)) {
if (length(grep("_2", colnames(Figure_5.8))) > 0) {
colnames(Figure_5.8) <- gsub("%", "\\\\%", colnames(Figure_5.8))
main_column_names <- colnames(Figure_5.8)[!grepl("_2", colnames(Figure_5.8))]
significance_column_names <- colnames(Figure_5.8)[grepl("_sig", colnames(Figure_5.8))]
presentation_column_names <-  main_column_names[!main_column_names %in% significance_column_names]

Figure_5.8 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Yes have children` = cell_spec(`Yes have children`, "latex", background = case_when(`Yes have children_sig` == "HIGHER" ~ "#00A3A3", `Yes have children_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`No children` = cell_spec(`No children`, "latex", background = case_when(`No children_sig` == "HIGHER" ~ "#00A3A3", `No children_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
Figure_5.8 %>%
kable("latex", col.names = gsub("blank", "", colnames(Figure_5.8)), escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters.")
}
```

```{r eval=eval_comparison}

asis_output(paste0("### ", comparison_table_title))
  
```

```{r eval=eval_comparison}
if (!is.null(Figure_5.8) && length(grep("_2", colnames(Figure_5.8))) > 0) {
comparison_column_names <- colnames(Figure_5.8)[grepl("_2", colnames(Figure_5.8))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_5.8 %>% select(tidyselect::all_of(colnames(Figure_5.8)[!colnames(Figure_5.8) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Yes have children` = cell_spec(`Yes have children`, "latex", background = case_when(`Yes have children_sig` == "HIGHER" ~ "#C3C3FF", `Yes have children_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`No children` = cell_spec(`No children`, "latex", background = case_when(`No children_sig` == "HIGHER" ~ "#C3C3FF", `No children_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", col.names = gsub("blank", "", presentation_column_names), escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
\pagebreak

