---
params:
  report_title: ""
  local_authority: ""
  year: ""
  topic_data: ""
  comparison_type: ""
  comparator: ""
title: "`r params$report_title`"
output:
  pdf_document:
    toc: yes
    fig_caption: false
header-includes:
    - \hypersetup{colorlinks=true, linkcolor = black, urlcolor = [RGB]{0, 163, 163}}
    - \usepackage{titling}
    - \pretitle{\begin{center}
      \includegraphics[width=2in,height=2in]{../www/new_logo.png}\LARGE\\}
    - \posttitle{\end{center}}
    - \renewcommand{\familydefault}{\sfdefault}
classoption: landscape
fontsize: 10pt
papersize: a4
geometry: margin=1.5cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
options(tinytex.verbose = TRUE)

library(knitr)
library(dplyr)
library(kableExtra)
library(png)
library(tidyselect)

local_authority <- params$local_authority
year <- params$year
topic_data <- params$topic_data
comparison_type <- params$comparison_type
comparator <- params$comparator

Figure_6.1 <- topic_data[[1]]
Figure_6.2 <- topic_data[[2]]
Figure_6.3 <- topic_data[[3]]
Figure_6.4 <- topic_data[[4]]
Table_6.1 <- topic_data[[5]]
Table_6.2 <- topic_data[[6]]
Figure_6.5 <- topic_data[[7]]
Figure_6.6 <- topic_data[[8]]

main_table_title <- paste0(local_authority, ", ", year)

eval_comparison <- ifelse(comparison_type == "No comparison", FALSE, TRUE)

eval_comparison_time_series <- ifelse(comparison_type == "Year" | comparison_type == "No comparison", FALSE, TRUE)

comparison_table_title <- if (comparison_type == "Local Authority") {
  paste0(comparator, ", ", year)
} else if (comparison_type == "Year") {
  paste0(local_authority, ", ", comparator)
} else {
  NULL
  }

```

## Acknowledgements
The Scottish Government acknowledges and thanks the 10,530
people across Scotland who gave their time to take part in the
Scottish Household Survey 2018.
This report was produced by the Scottish Household Survey Project Team
at the Scottish Government.
We would also like to thank all the Scottish Government lead analysts who
contributed to the project.
Finally, special thanks to Ipsos MORI and their interviewers for continuous
and relentless efforts during the fieldwork.

## Key

```{=latex}
$ \color[RGB]{0, 163, 163} \blacksquare $ Significantly higher $ \color[RGB]{195, 195, 255} \blacksquare $ Significantly lower
```
## Figure 6.1: How households are managing financially by year
### Column percentages, Households

### `r main_table_title`

```{r eval=(eval_comparison_time_series == FALSE)}
if (!is.null(Figure_6.1)) {
Figure_6.1 %>%
kable("latex", escape = TRUE, booktabs = T) %>% kable_styling(latex_options = "scale_down") %>% column_spec(1, width = "20em")
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_6.1)) {
if (length(grep("_2", colnames(Figure_6.1))) > 0) {
colnames(Figure_6.1) <- gsub("%", "\\\\%", colnames(Figure_6.1))
main_column_names <- colnames(Figure_6.1)[!grepl("_2", colnames(Figure_6.1))]
significance_column_names <- colnames(Figure_6.1)[grepl("_sig", colnames(Figure_6.1))]

Figure_6.1 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#00A3A3", `1999/2000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#00A3A3", `2001/2002_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#00A3A3", `2003/2004_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#00A3A3", `2005/2006_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#00A3A3", `2007/2008_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#00A3A3", `2009/2010_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#00A3A3", `2011_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#00A3A3", `2012_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#00A3A3", `2013_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#00A3A3", `2014_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#00A3A3", `2015_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#00A3A3", `2016_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#00A3A3", `2017_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#00A3A3", `2018_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em") %>% kable_styling(latex_options = "scale_down")
} else {
Figure_6.1 %>%
kable("latex", escape = TRUE, booktabs = T) %>% column_spec(1, width = "20em") %>% kable_styling(latex_options = "scale_down")
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison_time_series}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison_time_series}
if (!is.null(Figure_6.1) && length(grep("_2", colnames(Figure_6.1))) > 0) {
comparison_column_names <- colnames(Figure_6.1)[grepl("_2", colnames(Figure_6.1))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_6.1 %>% select(tidyselect::all_of(colnames(Figure_6.1)[!colnames(Figure_6.1) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1999/2000` = cell_spec(`1999/2000`, "latex", background = case_when(`1999/2000_sig` == "HIGHER" ~ "#C3C3FF", `1999/2000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2001/2002` = cell_spec(`2001/2002`, "latex", background = case_when(`2001/2002_sig` == "HIGHER" ~ "#C3C3FF", `2001/2002_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2003/2004` = cell_spec(`2003/2004`, "latex", background = case_when(`2003/2004_sig` == "HIGHER" ~ "#C3C3FF", `2003/2004_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2005/2006` = cell_spec(`2005/2006`, "latex", background = case_when(`2005/2006_sig` == "HIGHER" ~ "#C3C3FF", `2005/2006_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2007/2008` = cell_spec(`2007/2008`, "latex", background = case_when(`2007/2008_sig` == "HIGHER" ~ "#C3C3FF", `2007/2008_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2009/2010` = cell_spec(`2009/2010`, "latex", background = case_when(`2009/2010_sig` == "HIGHER" ~ "#C3C3FF", `2009/2010_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2011` = cell_spec(`2011`, "latex", background = case_when(`2011_sig` == "HIGHER" ~ "#C3C3FF", `2011_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2012` = cell_spec(`2012`, "latex", background = case_when(`2012_sig` == "HIGHER" ~ "#C3C3FF", `2012_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2013` = cell_spec(`2013`, "latex", background = case_when(`2013_sig` == "HIGHER" ~ "#C3C3FF", `2013_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2014` = cell_spec(`2014`, "latex", background = case_when(`2014_sig` == "HIGHER" ~ "#C3C3FF", `2014_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2015` = cell_spec(`2015`, "latex", background = case_when(`2015_sig` == "HIGHER" ~ "#C3C3FF", `2015_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2016` = cell_spec(`2016`, "latex", background = case_when(`2016_sig` == "HIGHER" ~ "#C3C3FF", `2016_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2017` = cell_spec(`2017`, "latex", background = case_when(`2017_sig` == "HIGHER" ~ "#C3C3FF", `2017_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2018` = cell_spec(`2018`, "latex", background = case_when(`2018_sig` == "HIGHER" ~ "#C3C3FF", `2018_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T) %>% column_spec(1, width = "20em") %>% kable_styling(latex_options = "scale_down")
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 6.2: How the household is managing financially by net annual household income
### Column percentages, Households
### Excludes Refused and Don't know

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_6.2)) {
Figure_6.2 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.2)) {
if (length(grep("_2", colnames(Figure_6.2))) > 0) {
colnames(Figure_6.2) <- gsub("%", "\\\\%", colnames(Figure_6.2))
main_column_names <- colnames(Figure_6.2)[!grepl("_2", colnames(Figure_6.2))]
significance_column_names <- colnames(Figure_6.2)[grepl("_sig", colnames(Figure_6.2))]

Figure_6.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Up to GBP15,000` = cell_spec(`Up to GBP15,000`, "latex", background = case_when(`Up to GBP15,000_sig` == "HIGHER" ~ "#00A3A3", `Up to GBP15,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`GBP15,001 to GBP30,000` = cell_spec(`GBP15,001 to GBP30,000`, "latex", background = case_when(`GBP15,001 to GBP30,000_sig` == "HIGHER" ~ "#00A3A3", `GBP15,001 to GBP30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Over GBP30,000` = cell_spec(`Over GBP30,000`, "latex", background = case_when(`Over GBP30,000_sig` == "HIGHER" ~ "#00A3A3", `Over GBP30,000_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Figure_6.2 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.2) && length(grep("_2", colnames(Figure_6.2))) > 0) {
comparison_column_names <- colnames(Figure_6.2)[grepl("_2", colnames(Figure_6.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_6.2 %>% select(tidyselect::all_of(colnames(Figure_6.2)[!colnames(Figure_6.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Up to GBP15,000` = cell_spec(`Up to GBP15,000`, "latex", background = case_when(`Up to GBP15,000_sig` == "HIGHER" ~ "#C3C3FF", `Up to GBP15,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`GBP15,001 to GBP30,000` = cell_spec(`GBP15,001 to GBP30,000`, "latex", background = case_when(`GBP15,001 to GBP30,000_sig` == "HIGHER" ~ "#C3C3FF", `GBP15,001 to GBP30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Over GBP30,000` = cell_spec(`Over GBP30,000`, "latex", background = case_when(`Over GBP30,000_sig` == "HIGHER" ~ "#C3C3FF", `Over GBP30,000_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 6.3: How the household is managing financially by household type
### Column percentages, Households
### Excludes Refused and Don't know

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_6.3)) {
Figure_6.3 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.3)) {
if (length(grep("_2", colnames(Figure_6.3))) > 0) {
colnames(Figure_6.3) <- gsub("%", "\\\\%", colnames(Figure_6.3))
main_column_names <- colnames(Figure_6.3)[!grepl("_2", colnames(Figure_6.3))]
significance_column_names <- colnames(Figure_6.3)[grepl("_sig", colnames(Figure_6.3))]

Figure_6.3 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Single adult / small adult small / Large adult` = cell_spec(`Single adult / small adult small / Large adult`, "latex", background = case_when(`Single adult / small adult small / Large adult_sig` == "HIGHER" ~ "#00A3A3", `Single adult / small adult small / Large adult_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Single parent / small family / large family` = cell_spec(`Single parent / small family / large family`, "latex", background = case_when(`Single parent / small family / large family_sig` == "HIGHER" ~ "#00A3A3", `Single parent / small family / large family_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Older smaller / Single older` = cell_spec(`Older smaller / Single older`, "latex", background = case_when(`Older smaller / Single older_sig` == "HIGHER" ~ "#00A3A3", `Older smaller / Single older_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Figure_6.3 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.3) && length(grep("_2", colnames(Figure_6.3))) > 0) {
comparison_column_names <- colnames(Figure_6.3)[grepl("_2", colnames(Figure_6.3))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_6.3 %>% select(tidyselect::all_of(colnames(Figure_6.3)[!colnames(Figure_6.3) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Single adult / small adult small / Large adult` = cell_spec(`Single adult / small adult small / Large adult`, "latex", background = case_when(`Single adult / small adult small / Large adult_sig` == "HIGHER" ~ "#C3C3FF", `Single adult / small adult small / Large adult_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Single parent / small family / large family` = cell_spec(`Single parent / small family / large family`, "latex", background = case_when(`Single parent / small family / large family_sig` == "HIGHER" ~ "#C3C3FF", `Single parent / small family / large family_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Older smaller / Single older` = cell_spec(`Older smaller / Single older`, "latex", background = case_when(`Older smaller / Single older_sig` == "HIGHER" ~ "#C3C3FF", `Older smaller / Single older_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 6.4: How the household is managing financially by tenure of household
### Row percentages, Households
### Excludes Refused and Don't know

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_6.4)) {
Figure_6.4 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.4)) {
if (length(grep("_2", colnames(Figure_6.4))) > 0) {
colnames(Figure_6.4) <- gsub("%", "\\\\%", colnames(Figure_6.4))
main_column_names <- colnames(Figure_6.4)[!grepl("_2", colnames(Figure_6.4))]
significance_column_names <- colnames(Figure_6.4)[grepl("_sig", colnames(Figure_6.4))]

Figure_6.4 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Does not manage well` = cell_spec(`Does not manage well`, "latex", background = case_when(`Does not manage well_sig` == "HIGHER" ~ "#00A3A3", `Does not manage well_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Gets by` = cell_spec(`Gets by`, "latex", background = case_when(`Gets by_sig` == "HIGHER" ~ "#00A3A3", `Gets by_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Manages well` = cell_spec(`Manages well`, "latex", background = case_when(`Manages well_sig` == "HIGHER" ~ "#00A3A3", `Manages well_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Figure_6.4 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.4) && length(grep("_2", colnames(Figure_6.4))) > 0) {
comparison_column_names <- colnames(Figure_6.4)[grepl("_2", colnames(Figure_6.4))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_6.4 %>% select(tidyselect::all_of(colnames(Figure_6.4)[!colnames(Figure_6.4) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Does not manage well` = cell_spec(`Does not manage well`, "latex", background = case_when(`Does not manage well_sig` == "HIGHER" ~ "#C3C3FF", `Does not manage well_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Gets by` = cell_spec(`Gets by`, "latex", background = case_when(`Gets by_sig` == "HIGHER" ~ "#C3C3FF", `Gets by_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Manages well` = cell_spec(`Manages well`, "latex", background = case_when(`Manages well_sig` == "HIGHER" ~ "#C3C3FF", `Manages well_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 6.1: How the household is managing financially by income sources
### Column percentages, Households
### Excludes Refused and Don't know

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_6.1)) {
Table_6.1 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_6.1)) {
if (length(grep("_2", colnames(Table_6.1))) > 0) {
colnames(Table_6.1) <- gsub("%", "\\\\%", colnames(Table_6.1))
main_column_names <- colnames(Table_6.1)[!grepl("_2", colnames(Table_6.1))]
significance_column_names <- colnames(Table_6.1)[grepl("_sig", colnames(Table_6.1))]

Table_6.1 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Main income from earnings` = cell_spec(`Main income from earnings`, "latex", background = case_when(`Main income from earnings_sig` == "HIGHER" ~ "#00A3A3", `Main income from earnings_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Main income from benefits` = cell_spec(`Main income from benefits`, "latex", background = case_when(`Main income from benefits_sig` == "HIGHER" ~ "#00A3A3", `Main income from benefits_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Main income from other sources` = cell_spec(`Main income from other sources`, "latex", background = case_when(`Main income from other sources_sig` == "HIGHER" ~ "#00A3A3", `Main income from other sources_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`An equal mix of income sources` = cell_spec(`An equal mix of income sources`, "latex", background = case_when(`An equal mix of income sources_sig` == "HIGHER" ~ "#00A3A3", `An equal mix of income sources_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_6.1 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_6.1) && length(grep("_2", colnames(Table_6.1))) > 0) {
comparison_column_names <- colnames(Table_6.1)[grepl("_2", colnames(Table_6.1))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_6.1 %>% select(tidyselect::all_of(colnames(Table_6.1)[!colnames(Table_6.1) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Main income from earnings` = cell_spec(`Main income from earnings`, "latex", background = case_when(`Main income from earnings_sig` == "HIGHER" ~ "#C3C3FF", `Main income from earnings_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Main income from benefits` = cell_spec(`Main income from benefits`, "latex", background = case_when(`Main income from benefits_sig` == "HIGHER" ~ "#C3C3FF", `Main income from benefits_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Main income from other sources` = cell_spec(`Main income from other sources`, "latex", background = case_when(`Main income from other sources_sig` == "HIGHER" ~ "#C3C3FF", `Main income from other sources_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`An equal mix of income sources` = cell_spec(`An equal mix of income sources`, "latex", background = case_when(`An equal mix of income sources_sig` == "HIGHER" ~ "#C3C3FF", `An equal mix of income sources_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Table 6.2: How the household is managing financially this year by gender and age of highest income householder
### Column percentages, Households
### Excludes Refused and Don't know

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Table_6.2)) {
Table_6.2 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Table_6.2)) {
if (length(grep("_2", colnames(Table_6.2))) > 0) {
colnames(Table_6.2) <- gsub("%", "\\\\%", colnames(Table_6.2))
main_column_names <- colnames(Table_6.2)[!grepl("_2", colnames(Table_6.2))]
significance_column_names <- colnames(Table_6.2)[grepl("_sig", colnames(Table_6.2))]

Table_6.2 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`Male` = cell_spec(`Male`, "latex", background = case_when(`Male_sig` == "HIGHER" ~ "#00A3A3", `Male_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Female` = cell_spec(`Female`, "latex", background = case_when(`Female_sig` == "HIGHER" ~ "#00A3A3", `Female_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`In another way` = cell_spec(`In another way`, "latex", background = case_when(`In another way_sig` == "HIGHER" ~ "#00A3A3", `In another way_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#00A3A3", `Refused_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#00A3A3", `16-39_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#00A3A3", `40-64_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#00A3A3", `65+_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Table_6.2 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Table_6.2) && length(grep("_2", colnames(Table_6.2))) > 0) {
comparison_column_names <- colnames(Table_6.2)[grepl("_2", colnames(Table_6.2))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Table_6.2 %>% select(tidyselect::all_of(colnames(Table_6.2)[!colnames(Table_6.2) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`Male` = cell_spec(`Male`, "latex", background = case_when(`Male_sig` == "HIGHER" ~ "#C3C3FF", `Male_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Female` = cell_spec(`Female`, "latex", background = case_when(`Female_sig` == "HIGHER" ~ "#C3C3FF", `Female_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`In another way` = cell_spec(`In another way`, "latex", background = case_when(`In another way_sig` == "HIGHER" ~ "#C3C3FF", `In another way_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`Refused` = cell_spec(`Refused`, "latex", background = case_when(`Refused_sig` == "HIGHER" ~ "#C3C3FF", `Refused_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`16-39` = cell_spec(`16-39`, "latex", background = case_when(`16-39_sig` == "HIGHER" ~ "#C3C3FF", `16-39_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`40-64` = cell_spec(`40-64`, "latex", background = case_when(`40-64_sig` == "HIGHER" ~ "#C3C3FF", `40-64_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`65+` = cell_spec(`65+`, "latex", background = case_when(`65+_sig` == "HIGHER" ~ "#C3C3FF", `65+_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 6.5: How households were managing financially by the Scottish Index of Multiple Deprivation
### Column percentages, Households
### Excludes Refused and Don't know

### `r main_table_title`

```{r eval=(eval_comparison == FALSE)}
if (!is.null(Figure_6.5)) {
Figure_6.5 %>%
kable("latex", escape = TRUE, booktabs = T)
 } else {
        asis_output("### There is no data to show for this table within the specified parameters")
      }
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.5)) {
if (length(grep("_2", colnames(Figure_6.5))) > 0) {
colnames(Figure_6.5) <- gsub("%", "\\\\%", colnames(Figure_6.5))
main_column_names <- colnames(Figure_6.5)[!grepl("_2", colnames(Figure_6.5))]
significance_column_names <- colnames(Figure_6.5)[grepl("_sig", colnames(Figure_6.5))]

Figure_6.5 %>% select(tidyselect::all_of(main_column_names)) %>%
mutate(`1 - 20pc most deprived` = cell_spec(`1 - 20pc most deprived`, "latex", background = case_when(`1 - 20pc most deprived_sig` == "HIGHER" ~ "#00A3A3", `1 - 20pc most deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#00A3A3", `2_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#00A3A3", `3_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#00A3A3", `4_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF")),
`5 - 20pc least deprived` = cell_spec(`5 - 20pc least deprived`, "latex", background = case_when(`5 - 20pc least deprived_sig` == "HIGHER" ~ "#00A3A3", `5 - 20pc least deprived_sig` == "LOWER" ~ "#C3C3FF", TRUE ~ "#FFFFFF"))

) %>%
select(!tidyselect::all_of(significance_column_names)) %>%
kable("latex", escape = FALSE, booktabs = T)
} else {
Figure_6.5 %>%
kable("latex", escape = TRUE, booktabs = T)
}
} else {
  asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
```{r eval=eval_comparison}
asis_output(paste0("### ", comparison_table_title))
```

```{r eval=eval_comparison}
if (!is.null(Figure_6.5) && length(grep("_2", colnames(Figure_6.5))) > 0) {
comparison_column_names <- colnames(Figure_6.5)[grepl("_2", colnames(Figure_6.5))]
comparison_rename_column_names <- gsub("_2", "", comparison_column_names)

Figure_6.5 %>% select(tidyselect::all_of(colnames(Figure_6.5)[!colnames(Figure_6.5) %in% comparison_rename_column_names])) %>%
rename_at(comparison_column_names, ~ comparison_rename_column_names) %>%
mutate(`1 - 20pc most deprived` = cell_spec(`1 - 20pc most deprived`, "latex", background = case_when(`1 - 20pc most deprived_sig` == "HIGHER" ~ "#C3C3FF", `1 - 20pc most deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`2` = cell_spec(`2`, "latex", background = case_when(`2_sig` == "HIGHER" ~ "#C3C3FF", `2_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`3` = cell_spec(`3`, "latex", background = case_when(`3_sig` == "HIGHER" ~ "#C3C3FF", `3_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`4` = cell_spec(`4`, "latex", background = case_when(`4_sig` == "HIGHER" ~ "#C3C3FF", `4_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF")),
`5 - 20pc least deprived` = cell_spec(`5 - 20pc least deprived`, "latex", background = case_when(`5 - 20pc least deprived_sig` == "HIGHER" ~ "#C3C3FF", `5 - 20pc least deprived_sig` == "LOWER" ~ "#00A3A3", TRUE ~ "#FFFFFF"))) %>%
        select(!tidyselect::all_of(significance_column_names)) %>%
        kable("latex", escape = FALSE, booktabs = T)
} else {
asis_output("### There is no data to show for this table within the specified parameters, or there is no data to compare with.")
}
```
## Figure 6.6: Households who manage well financially by deprivation over time
### Base numbers at local authority level are too small to produce robust analysis.
