---
title: "Chapter 2: The Composition and Characteristics of Households in Scotland"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)

library(knitr)
library(kableExtra)

local_authority <- params$local_authority
year <- params$year
chapter_data <- params$chapter_data

Table_2.1 <- chapter_data[[1]]
Table_2.2 <- chapter_data[[2]]
Table_2.3 <- chapter_data[[3]]
Figure_2.1 <- chapter_data[[4]]
Figure_2.2  <- chapter_data[[5]]
Table_2.4_Figure_2.3 <- chapter_data[[6]]
Table_2.5 <- chapter_data[[7]]
Table_2.6 <- chapter_data[[8]]
Figure_2.4 <- chapter_data[[9]]
Table_2.7 <- chapter_data[[10]]
Figure_2.5 <- chapter_data[[11]]
Table_2.8 <- chapter_data[[12]]
Table_2.9 <- chapter_data[[13]]
Table_2.10 <- chapter_data[[14]]
Table_2.11 <- chapter_data[[15]]
Table_2.12 <- chapter_data[[16]]
Table_2.13 <- chapter_data[[17]]
Table_2.14 <- chapter_data[[18]]
Table_2.15 <- chapter_data[[19]]
Table_2.16 <- chapter_data[[20]]
Table_2.17 <- chapter_data[[21]]
```

# `r paste0(local_authority, ", ", year)`

## Table 2.1: Age of all household members by year	
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.1) %>%
kable_styling(latex_options = "scale_down")
```

## Table 2.2: Gender of all household members by year	
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.2) %>%
kable_styling(latex_options = "scale_down")
```
## Table 2.3: All household members with a long-term physical or mental health condition by year	
### Column percentages, Adults	
### This question was changed in 2014, so this data is no longer comparable with previous years. Therefore, 2013 data is not presented here.	
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.3) %>%
kable_styling(latex_options = "scale_down")
```
##   Figure 2.1: Age of adults by year	
### Column percentages, Adults

```{r}
kable(Figure_2.1) %>%
kable_styling(latex_options = "scale_down")
```
##   Figure 2.2: Gender of adults by year	
### Column percentages, Adults

```{r}
kable(Figure_2.2) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.4, Figure 2.3: Adults with a long-term physical or mental health condition by year	
### Column percentages, Adults	
### The question asked in its current form was introduced in 2012 and so not directly comparable with the previous years
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.4_Figure_2.3) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.5: Ethnicity of adults by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.5) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.6: Economic status of all adults aged 16-64
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.6, row.names = FALSE) %>%
kable_styling(latex_options = "scale_down")
```
## Figure 2.4: Economic status of adults by year - selected groups
### Column percentages, Adults

```{r}
kable(Figure_2.4) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.7: Sexual orientation of adults by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.7) %>%
kable_styling(latex_options = "scale_down")
```
##   Figure 2.5	Religious belonging of adults by year	
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Figure_2.5) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.8: Marital status of adults by year
### Column percentages, Adults
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.8) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.9: Current marital status of adults by age	
### Column percentages, Adults

```{r}
kable(Table_2.9) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.10: Age of adults by marital status	
### Row percentages, Adults

```{r}
kable(Table_2.10) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.11: Household type of households by year	
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.11) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.12: Households with children by year	
### Column percentages, Households

```{r}
kable(Table_2.12) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.13: Property type of households by year	
### Column percentages, Households

```{r}
kable(Table_2.13) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.14: Tenure of households by year	
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.14) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.15: Scottish Index of Multiple Deprivation of households by year	
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.15) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.16: Urban rural split of households by year
### Column percentages, Households
### [Another breakdown of this table can be found at the Scottish Surveys Core Questions](https://www2.gov.scot/Topics/Statistics/About/Surveys/SSCQ)

```{r}
kable(Table_2.16) %>%
kable_styling(latex_options = "scale_down")
```
##   Table 2.17: Household income of households by year	
### Column percentages, Households
```{r}
kable(Table_2.17) %>%
kable_styling(latex_options = "scale_down")
```
